% Created 2021-09-11 Sat 08:17
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley it}
\date{\today}
\title{Hist Day one}
\hypersetup{
 pdfauthor={Huxley it},
 pdftitle={Hist Day one},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\texttt{make sure to have arta rank our heights!} \#\# How to Read - Focus on big
picture - \textbf{Don't} worry about remembering dates - \textbf{Do} Focus on Trends,
patterns, main points.

\section{\#\# The Modern World}
\label{sec:org42419b5}
\subsubsection{Scope}
\label{sec:org846fa98}
\begin{itemize}
\item To broad to focus on all

\begin{itemize}
\item Roughly 1500
\item End at the cold war
\item Four regions hold most of the people

\begin{itemize}
\item Europe, East Asia, South Asia, Middle East.
\end{itemize}
\end{itemize}
\end{itemize}

\texttt{INTERACTION BETWEEN STATES}

\begin{quote}
heres a qoute!
\end{quote}

\subsection{What we will cover}
\label{sec:org0e5eaad}
\begin{enumerate}
\item Hegemony
\item Balance of power -> global order
\item Ideologies and tech
\item Disruption of balance, WW1 aftermath
\item Disruption of balance part two, barley boogalo. Ft. Fascism,
Communism, WW2.
\item Bipolar world, cold war
\end{enumerate}

\subsection{Key Skills}
\label{sec:org863e242}
\begin{itemize}
\item General and specific causes of events
\item Using + evaluating evidence
\item construct arguments
\item Learn to write well
\item \{Some other stuff\}
\end{itemize}

\section{Freewrite time?!?}
\label{sec:org11983f4}
\begin{quote}
What are the top six most powerful countries in the world? \emph{Arta}
\end{quote}

\texttt{define power as: influence over other countries} - important, according
to arta \^{} \emph{in relation to other countries}

military power not as important anymore

\begin{enumerate}
\item China -> Huge amount of people, resources, millitary. Govermental
system allows for easy control and progress. Ie. building a hospital
in three days. + trade leverage
\item North Korea. -> Power by insanity. Nixon (I think) once made the
argument that other countries will be more wary / respect the wishes
of countries with people in office that are \emph{crazy}, because they
will do anything. Kimmy is that crazy man.
\item USA -> Lots of resources, I don't really know how we compare as I am
infested with propaganda.
\item India. Massive amount of people, growing insanely quickly. Will be
much more powerful very soon.
\item Russia -> Idrk, look at the election? Powerful meddling
\end{enumerate}

\textbf{\emph{nukes make things weird}}

Focus on transitions in this course

\subsection{How did someone in the 1500s define power?}
\label{sec:org53226c0}
\href{https://nuevaschool.instructure.com/courses/2821/modules/items/174842}{Reading}
Machiavelli's ideas: - How do his ideas of strength compare to yours? -
How relevant are his ideas today? - if not, how has the world changed to
make them so? - if so, how has the world stayed the same to make them
so?

\begin{quote}
If Mercenary captains are capable men, then you cannot trust them,
because they always aspire to their own greatness. But if the captain
is not skilful, you are ruined in the usual way.
\end{quote}

\begin{enumerate}
\item BRD (Breakout Room Discussion)
\label{sec:orgb6166ea}
Less true with more bureaucracy in modern day

\noindent\rule{\textwidth}{0.5pt}

Drones are very important, they control skies, and their pilots don't
die when their drones do, they get better. \emph{Remote} is a massive deal.
\end{enumerate}
\end{document}
