% Created 2021-09-11 Sat 09:36
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{China's Decline w.r.t Reopening}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={China's Decline w.r.t Reopening},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{China's Decline: Reopening and Trade}
\label{sec:org5f6ebb0}
After closing down trade after the ending of
\href{KBhHIST201ZhengHeSeafaring.org}{KBhHIST201ZhengHeSeafaring}
Zheng He's missions, Ming's goverment decided to reopen after yet
another few change of leadership. The long wait until reopening, and the
way reopening happened, was quite problematic. It, even after a somewhat
free economy, caused
\href{KBhHIST201ChinasDeclineWRTCurrency.org}{KBhHIST201ChinasDeclineWRTCurrency}
Currency problems.

\href{KBhHIST201MannMing.org}{KBhHIST201MannMing} (C. Mann's) 1500s
Ming

\subsection{External Factors}
\label{sec:org6e146fe}
\begin{itemize}
\item Europe is "worthy" of trading with
\item Americas, which, \emph{surprise!}, actually exists
\item Realized that, \emph{surprise!} internal control of trade does not actually
controlled the economy

\begin{itemize}
\item Attempted to control trade exclusively for government. That
backfired:

\begin{itemize}
\item Used system of Ban-And-Tribune (trade is banned, gifts, however,
are allowed)
\item Empire lost control of coinage
\item No longer had silver backing
\href{KBhHIST201ChinasDeclineWRTCurrency.org}{KBhHIST201ChinasDeclineWRTCurrency}
\end{itemize}
\end{itemize}
\end{itemize}

\subsection{Domestic Factors}
\label{sec:org7364f48}
\href{KBhHIST201MannMing.org}{KBhHIST201MannMing} (C. Mann's) 1500s
Ming

With attempting to control the trade and shutting down maritime traders,
stuff kept going wrong.

\begin{itemize}
\item Had weak navy at that point due to logic that "if trade not happening
why protect it" => caused widespread smuggling

\begin{itemize}
\item Struggling people turned to trade deux. smuggling
\item Fujian worst affected by piracy --- most poor

\begin{itemize}
\item Nothing for them on land
\item Originally depended on trade
\item Yuejiang worst affected out of all regions

\begin{itemize}
\item 24-Generals assumed control of trade
\item Split market up and each controlled a region
\item Could not be dislodged by 300 imperial soldiers\\
\end{itemize}

\item Commissioner could not deal with it anymore and tried to bribe.
That didn't work.
\item Eventually, emperor capitulated, and, guess what, we began trading
again.
\item But! Shock surprise, that brought with it a host of problems,
namely
\href{KBhHIST201ChinasDeclineWRTCurrency.org}{KBhHIST201ChinasDeclineWRTCurrency}
China's Decline w.r.t. Currency
\end{itemize}
\end{itemize}
\end{itemize}
\end{document}
