% Created 2021-09-11 Sat 09:36
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{WWI, the war}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={WWI, the war},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{WWI, the War}
\label{sec:orgb476981}
\textbf{The War Triggered: a bosnian revolutionary killed the heir to the
Habsburg empire.}

CLAIM: the newly selected emperor would have favored and equated the
Slavs, but revolutionaries want to fight so he was killed. For
background, see
\href{KBhHIST201WWITriggering.org}{KBhHIST201WWITriggering}

\subsection{"Blank-check"}
\label{sec:org9fe5067}
Asking for advice on the actual possibility of support, Austria
basically recieved a "blank check" from Germany to do whatever they want
to resolve The slavic issue.

The Russians on the other side persuaded France to also issue them
"blank-check" style backing to protect their protecterate with the
slavs.

\subsection{Feces intersects with the fan}
\label{sec:org71a7e0a}
Serbs rejected Austrian ultimatum, and so the two started fighting.
Because Germany will eventually step in, Russia began provoking Germany.
Expecting France to step in anyways, Germany than declared war an France
by attacting the neutral Belgian protecterate. And so now, ladies and
gentlemen, we have a world war.

\noindent\rule{\textwidth}{0.5pt}

Sidenote:

\begin{itemize}
\item The Germans hoped that England will not fight in the wars.
\item CLAIM: had Germany know England would fight, the war may have not
come.
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

But then,

\subsection{England Joins}
\label{sec:orgca212ff}
\emph{When Germany violated Belgian neutrality, England declared war on it
immediately.}

\begin{itemize}
\item CLAIM: beacuse Europe was divided by two camps, anything of any
significance that occured was a test of strength between the two camps
with winners and loosers. Hence, each incident garanteed the next.
Germany vs. france
\item The Germanic dread of it being encircled by France and Russia caused
them to prefer war to break their landlocked status. France feared of
Germanic industry and wanted to work with Russia. Russia vs. Austria
\item Russians and Austrians were both having losing empires which lead to
the administration of both parties being increasingly despereate.
\end{itemize}

\textbf{CLAIM: WWI --- backwards parts of Europe dragging advanced societies
into ruin.}

\subsection{The War war}
\label{sec:org98783d5}
See different countries' war plans here:
\href{KBhHIST201WWIStrategies.org}{KBhHIST201WWIStrategies}
\end{document}
