% Created 2021-09-11 Sat 08:17
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Global History, Intro}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Global History, Intro},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\textbf{Goal}: how did the global history influence and cause us to end up
where we are today?

\begin{quote}
History as familiar? vs. History as foreign? vs. History as present?
\end{quote}

\emph{Curiosities from history}

\begin{itemize}
\item Gender worked differently
\item "Horsemanning" => an early form of memeary
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

\section{History as the reflection of the present}
\label{sec:org4016f3c}
\begin{quote}
As these countries move forward in time, they could become
interdependent
\end{quote}

\begin{itemize}
\item Events in history could reflect examples for the present
\end{itemize}

\section{Big questions}
\label{sec:orgebe6730}
\begin{itemize}
\item When did world history became "global history"?
\item What forces connected the various regions in the world?
\item Since when and in what parts did world history became the history of
the West?

\begin{itemize}
\item Where is the West, anyways?
\item How do you define the West? \# The Class \#\# Calendar/Course Outline
\end{itemize}

\item Unit 1: Empires
\item Unit 2: Europe
\item Unit 3: Imperialism
\item\relax [break]
\item Unit 4: WWI
\item Unit 5: WWII
\item Lit Review Paper
\item Unit 6: Cold War
\end{itemize}

\section{Expectations}
\label{sec:org0af5aa2}
These will probably be not very useful except for people taking HIST201
with Sushu. Nevertheless, this
\href{KBhHIST201SushuCourseExpectation.org}{KBhHIST201SushuCourseExpectation}
is Sushu's course expectations.
\end{document}
