% Created 2021-09-11 Sat 08:17
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Hist Day One}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Hist Day One},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#flo \#ref \#ret \#disorganized \#incomplete

\noindent\rule{\textwidth}{0.5pt}

\section{Here. We. Go.}
\label{sec:org76a6c7c}
\begin{itemize}
\item Why does war exist? Are they products of failure in other realms or
logical products of global systems?

\begin{itemize}
\item war has heavy economic benifits -- war is heaviliy profitable
\item war for resources, war for morality -- "this is right, and we will
fight for it!"

\begin{itemize}
\item I missed this: war for social cohession? whats the broader
catagory?
\end{itemize}

\item also war for resources disuised as war for morality
\end{itemize}

\item What would be required to put an end to war?

\begin{itemize}
\item heaviliy dependent on the war, and the nature of the war.

\item very importyant question. one side conceding would do it.

\item running out of financial resource? end by exaustion?

\item wars end when one side gives up (not when one side wins).

\item I READ TRHE QUESTION WRONG: I read it as a war

\item war the way we know it is ending, due to MAD.
\end{itemize}

\item Is there such a thing as a just (or good, ethical, righteous) war?
Why/why not?

\begin{itemize}
\item this is not a question i am prepared to answer while still debating
the very meaning of 'good.'
\item utilitarian perspective, if the war reduces overall pain or
suffering (bad?) then yes, it is good.
\item if going to war is the choice of the people, ..
\item 
\end{itemize}
\end{itemize}

\begin{verbatim}
**In groups, discuss and compare your ideas on the origins of war, the possibilities of its eradication, and its justness/unjustness. 

Look for points of agreement and disagreement and be prepared to share.**
\end{verbatim}
\end{document}
