% Created 2021-09-11 Sat 08:18
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Mason Ch. 10}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Mason Ch. 10},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#flo \#ref \#disorganized \#incomplete

\noindent\rule{\textwidth}{0.5pt}

\section{Title!}
\label{sec:org4c69704}
bolshevik revolution got russia out of the world war? (and europe)?

and into communim!

US didnt trust it

after allieing in ww2, and emerging as the two superpowers, cold war
happens!

why did the revolt happen?

russia was despotic, stuck in old ruling systems, and had slow economic
change, ect. not much of an urban working class, which marx needs

marxim starts rising, for a few reason on pg 58

split into two group: bolshevik and mensheviks, wanting quick rev and
gradual aproach

since the proletariat was small, lenin wanted to make an elite vanguard

lenin didnt want to wait for capitalim to fail, he just wanted to kip it
entirely. fuedualism -> communism

lenin said that imperialism is the highest stage of capitalism

bolzhevik didnt do alot, and the 'communim' that emerged was not at all
marxist theory (again).

rasputin can stop the bleeding of the hemophiliac son with hypnosis?
\end{document}
