% Created 2021-09-11 Sat 08:17
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Palmer and Weitz on Weimar Republic}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Palmer and Weitz on Weimar Republic},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#flo \#ref \#disorganized \#incomplete

\noindent\rule{\textwidth}{0.5pt}

\section{Weimar Republic.}
\label{sec:orga780372}
spengler had cool historical theories with a massive amount of
explanability

dadaism, rejcted the traditional

poem, the second coming:

” The best lack all conviction, while the worst

Are full of passionate intensity. ” jeez.

russia was ostrozised,

everyone revered woodrow wilson

\begin{quote}
greeted as the man who would lead civilization out of its wasteland.
\end{quote}

democracy!

\begin{quote}
Democracy having defeated the Central Powers, people hoped that a new
settlement, made in a democratic age, might be reached by gen eral
agreement in an atmosphere of mutual confidence. There was a real
sense of a new era.
\end{quote}

allies banded together and follows wilson,

everyone made a bunch of treaties

nationalism was big, worked well with liberalism and democracy

stuff started going wrong

league of nations! international anarchy, no more! (ish)
\end{document}
