% Created 2021-09-11 Sat 09:35
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Bio Self Eval}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Bio Self Eval},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#ret

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
Hi All, 

Please share with me what aspects of biology class content you found particularly interesting and think you will remember forever. 


Please reflect on your study habits and your ability to navigate this style of teaching.

What did you do well and what could you have done better? What are examples of ways you overcame some struggles?
\end{verbatim}

Biology class felt like getting plunged into a sea of knowledge. It was
not easy to understand everything we were getting taught to the level
that I would like to. To deal with this, I would often spend time going
back over the presentations and doing research on the topics.

Another struggle was figuring out how to sort the knowledge I gained in
my deep dive. To learn about my deep dive topic, I would simply do
research online, letting my curiosity drive where I would go next. Of
course research must be driven by curiosity, but when researching for a
project, the research is also guided by the end goal of the project.
Trying to funnel the learning that I gained driven purely by curiosity
into a project was a challenge, and I ended up only being able to
include a small fraction of what I learned in my final project.

Regardless, even if I didn't get to include all of my learning in my
final project, I still learned a lot and enjoyed doing so.
\end{document}
