% Created 2021-09-27 Mon 11:51
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Taproot}
\date{\today}
\title{LinApprox + Differentials Quiz\\\medskip
\large Let's do this.}
\hypersetup{
 pdfauthor={Taproot},
 pdftitle={LinApprox + Differentials Quiz},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents


\section{Implicit Differentiation}
\label{sec:orgdcc1e2a}
The usual process:
\begin{enumerate}
\item Differentiate everything with respect to x
\item Apply the chain rule to functions left in the mix: since \((f(g(x)))' = g'(x) f'(g(x))\), \(\frac{d}{dx}y^2 =  \frac{dy}{dx}y^2\).
\item Apply algebra to get \(\frac{dy}{dx}\) on one side.
\item OPTIONAL(?): Convert back to explicit form by plugging in value of \(y\).
\end{enumerate}

\subsection{Common Problems and their Respective Approaches}
\label{sec:org04c6d5c}
\subsubsection{Find the equation of the tangent/normal at (A,B)}
\label{sec:org0f886af}
Remember that \(L(a) = f(a) + f'(a)(x-a)\), and that'll give you tangent.
Normal line is just perpendicular of tangent, so \(\frac{-1}{L(a)}\).
\subsubsection{Find location of curve where tangent is \emph{vertical}}
\label{sec:org2e01fe1}
Simply find what values of x and y make the tangent go to infinity.
System of equations with the derivative and the original implicit equation itself. You can make this faster with fractions by only using denom/numerator.
\subsubsection{Find location of curve where tangent is \emph{horizontal}}
\label{sec:org33757b0}
Same as above but solve for what makes tangent go to zero.
\subsection{Misc Tips}
\label{sec:org9ee3e66}
\subsubsection{Pay attention to the original equations!}
\label{sec:org087317d}
They're very useful in algebra!

\section{Derivatives of Inverse Functions}
\label{sec:org28d2f7a}
Formula for this is \((f^{-1}(x))' = \frac{1}{f'(f^{-1}(x))}\). 

\section{Derivatives of Inv. Trig Functions}
\label{sec:orge96254f}
Remember the derivs

\subsection{{\bfseries\sffamily TODO} Explicitly deriving}
\label{sec:orgbc4aad1}

\section{Linear Approximations}
\label{sec:orgdab888a}
\(L(a) = f(a) + f'(a)(x-a)\)
Plug in for appropriate a, and manually check for over/underestimation if problem asks.

\subsection{{\bfseries\sffamily TODO} Algebraically getting set accuracy bounds}
\label{sec:org0447746}

\section{Differentials}
\label{sec:orgd3d0784}
\(dy = f'(x)dx\)

\(-dx < dy < dx\)
\end{document}
