% Created 2021-09-27 Mon 11:52
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Colonial America}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Colonial America},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents


\section{Talking about the Essay}
\label{sec:org36edb67}
See \href{KBhIntersectionsEssayPrep.org}{Intersection Essay Prep}.

\subsection{File Organization}
\label{sec:orgc92f720}
\begin{itemize}
\item Take a look at "Colonial America, notes", which are the notes of the class
\item A PDF of the slides are also available
\end{itemize}

\subsection{When is the draft due?}
\label{sec:org69d3285}
IDK. He still won't tell. :(

\section{European Colonization}
\label{sec:orgdb5565f}
A "world-wide imperial contest", a global political competition. Not primarily motivated by spreading \emph{democracy}, its about Monies.

\begin{itemize}
\item Spanish: started the conquest, for the Spanish armada
\item English: bubbling, for minor economic modivation
\item French: interested in fur, and trying to maximize gain and investment
\end{itemize}

So, compare and contrast the three systems.

\section{Voyages of Discovery}
\label{sec:orgfd4d391}

\subsection{Motivations}
\label{sec:org232fc59}
\begin{itemize}
\item Rise of a \emph{business} oriented class
\item Pooling of resources for investment
\item Tech: astrolabe, maps, compass, better ships, etc.
\end{itemize}

\subsection{Mercantilism}
\label{sec:orgf81df95}
A pair-relationship between colonies:

\begin{itemize}
\item Mother Country provides\ldots{}
\begin{itemize}
\item Finished products
\item Protection
\item Governance
\end{itemize}
\item Colonies provides\ldots{} 
\begin{itemize}
\item Raw materials
\item Monopolies on market
\item Loyalty
\end{itemize}
\end{itemize}

\section{Colonizers}
\label{sec:org64bf7bf}

\subsection{Russians!}
\label{sec:org68f3b4d}
Russia traveling from west => east; competing with the northern going group.

\subsection{Spain!}
\label{sec:org674912a}
"Superpower" built upon the Spanish Navy (the "armada.")

\begin{itemize}
\item Mission: churches religions and cultures (supposed to be self-sufficient)
\item Presidio: military gates and posts
\item Pueblos: living
\end{itemize}

\subsubsection{Goals}
\label{sec:org0500033}
\begin{itemize}
\item Find Gold!
\item Acquire Land!
\item Develop Trade!
\item Christian conversion (mostly to get papal decree
\end{itemize}

\subsubsection{Weaknesses}
\label{sec:orgfc31260}
\begin{itemize}
\item Spanish empire stretched pretty thin
\item Did not allow others to come trade, which means limited trade
\end{itemize}

\subsection{England!}
\label{sec:org66a88ac}
Leveraged \textbf{Privateers}: pirates with royal decrees, to destroy ability. Defeated the armada by chasing them and sticking them into the English isle.

All business adventures to make money. Settlers were not as loyal because there were a group of dissidents, beggars, and ex-convicts. Also, they are not motivated by missionary reasons.

\subsection{France}
\label{sec:org461b742}
French along the river systems. Everything flows from the river systems.

Based on \textbf{trade} rather than \textbf{architecture}. Leveraged the Fur Trade as the primary exclusive source of income.

\section{Colonized}
\label{sec:org8e294a4}
\begin{itemize}
\item No respect for Native American cultures or strategies of land use
\item Every mission courtyard had a place where those who disobeyed where wipped
\item Father Junipero Serra: think that the native were "childlike" and required education

\noindent\rule{\textwidth}{0.5pt}
\end{itemize}

\section{Colonial America, the Thirteen American Colonies}
\label{sec:org3245c05}
The original British colonies sucked. The English didn't want for them to trade with each othere, but with England.

Oh by the way: Florida was \emph{not} the Thirteen Colonies


\subsection{Jamestown, Virginia}
\label{sec:org4118bbd}
1607, John Smith's colonies. It was a Charter colony, it was a business by the order of the Crown.

\begin{itemize}
\item 50\% Mortality in Year 1
\item Not self sufficient: hunting gold instead of deer, did not plant enough
\item Too many "gentlemen", not enough laborers. Smith: "He how will not work shall not eat."
\end{itemize}

John Rolfe introduces \textbf{tobacco}: provides economic foundation for Virginia. Tobacco causes cancer, and so if Barry catches you smoking he will\ldots{}.

\begin{itemize}
\item 1619: House of Burgesses formed; 1st elected representative body in North America
\item 1619: First Africans sold; indentured servants became racialized
\item 1622: Powhatan attack the settlement
\item 1624: Crown buys Jamestown; it becomes a "Crown Colony"
\end{itemize}

\subsubsection{Bacon's Rebellion}
\label{sec:orgc89d6e7}
Jamestown grew rapidly b/c of tobacco. Willian Berkeley proceeds to corrupt the House of Burgesses to restrict political rights to landowners.

Nathaniel Bacon had a \emph{coup d' etat} against Berkeley.

\textbf{\textbf{Significance}}: illuminates growing sociopolitical tensions between landless men vs. those in power.

\subsection{The Mayflower}
\label{sec:org255d0d3}
Group of other "Pilgrims" arriving in the new New World. Agree to create a covenant, promising to obey" just and equal laws."

\begin{itemize}
\item "Covenant and combine ourselves together in a \textbf{\textbf{civil body politic}}"
\item "Enact, constitute, and frame just and equal laws"
\end{itemize}

\subsection{Puritan's Colonies: Massachusetts Bay}
\label{sec:org3fcc064}
Massachusetts Co. Puritan's Goal: establish a "City of God."

\begin{itemize}
\item Wanted to setup a Puritan colony that allow
\item Lack of religious toleration: forced the Quakers to leave
\end{itemize}

Puritans planted food to support the growth of these colonies.

\subsubsection{From Massachusetts and Plymouth}
\label{sec:orgd4d2789}
Plymouth is a basis for the subsequent settlement of\ldots{}

\begin{itemize}
\item Rhode Island
\item Connecticut
\item Now Hampshire
\item Maine
\end{itemize}

\subsubsection{Structure of Settlements}
\label{sec:orga569f6b}
\begin{itemize}
\item Members bounded by covenants
\item Houses \& Meeting house laid in common pasture
\item "Selectmen" elected to do roles
\end{itemize}

\subsubsection{Puritans' System' Problems}
\label{sec:org13f55a2}
Communism doesn't work b/c there is a fundamental lack of trust between human communities.

\begin{itemize}
\item Didn't value religious differences
\item ()? Became royal colonies
\end{itemize}

\subsubsection{Religious Differences}
\label{sec:org87ed515}
\begin{center}
\begin{tabular}{ll}
Puritans & Quakers\\
\hline
Predestination & Nonviolence\\
Conversion & God exists in all men\\
\end{tabular}
\end{center}

\subsection{Connecticut}
\label{sec:orgc2a1a27}
Settlers from Massachusetts bay looking for more land. Received charter to elect their own governor.

\subsection{New Netherlands (NY)}
\label{sec:orga7ac400}
Dutch established the Patroon system: land granted for bringing new settlers. Crown awards land to Lord York after defeat of Dutch.

\subsection{New Sweden (Delaware)}
\label{sec:orgd14d686}
Also gave to lord York somehow?

\subsection{New Jersey and Pennsylvania}
\label{sec:org4c24324}
Sold land to the Quakers. As a thank you to the William Penn, who gave the Quakers' land, they:

\subsubsection{Pennsylvania's System}
\label{sec:org8e1a5ea}
\begin{itemize}
\item Established a liberal frame of government with assembly
\item Good relations with Native Americans - "Paid for Land"
\item Had no army, believed in peace
\end{itemize}

\subsubsection{Philadelphia}
\label{sec:org52670e8}
\begin{itemize}
\item City laid out as a grid
\item Established the first model for urban planning in many colonies
\end{itemize}

\subsection{Maryland}
\label{sec:org9a0964f}
Catholic colony. Had religious toleration after realizing the Puritans came swooping in.

\subsection{Carolina}
\label{sec:orgf840251}
1663, chartered by the crown. Planned to attract settlers with religious \& political freedom. Central to the trading of slavery.

\subsection{Georgia}
\label{sec:org3307195}
Buffer zone between Carolina (productive slave trading region) and Spanish Florida

\begin{itemize}
\item Attempted to create Utopian societies
\item \ldots{} but failed
\end{itemize}

\section{Emergence of Colonies}
\label{sec:orgd58e93d}
I need notes from someone here.

\begin{itemize}
\item Expansion towards west
\item Concentration of agriculture in the south
\begin{itemize}
\item Cotton
\item Tobacco
\item Cotton => created technology to fluffy cottons
\end{itemize}
\end{itemize}

Lots of \textbf{\textbf{tax}} from the British. Individuals bitter about the large industry in England compared to the large raw products form the Americas.

\subsection{The Deed of Gift of Robert Carter}
\label{sec:org6baae4f}
Begin \emph{manumission}: began freeing slaves in 1791, one of the first emancipators.

=> A lot of racial tensions were allowed to continue and contributed to the problem

\subsection{Port Cities}
\label{sec:org924c30b}
Port cities grew bigger and became hubs of cultural and political activity.

\begin{itemize}
\item Revolutionary sparks occurred first at big cities \{Boston, Philly, NYC\}
\item Served as industrial centers
\item Increased education
\end{itemize}


\section{The Seven Year's War}
\label{sec:orgff0428b}
\href{KBhFrenchAndIndian.org}{French and Indian War}

\section{And so, explain}
\label{sec:org5d23d32}
\begin{itemize}
\item What characteristics do these colonies have in common?
\item What relationships were building between the colonies and the crown
\item What "roots" of democracy emerged?
\item What "American" values emerge
\end{itemize}
\end{document}
