% Created 2022-05-26 Thu 22:22
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{tikz}
\usepackage{cancel}
\usepackage{pgfplots}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\usepackage{csquotes}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

n \textbf{*}

\begin{verbatim}
<g.C />
\end{verbatim}

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
import { Canvas, useFrame } from 'https://cdn.skypack.dev/react-three-fiber'

function Box(props) {
  // This reference gives us direct access to the THREE.Mesh object
  const ref = useRef()
  // Hold state for hovered and clicked events
  const [hovered, hover] = useState(false)
  const [clicked, click] = useState(false)
  // Subscribe this component to the render-loop, rotate the mesh every frame
  useFrame((state, delta) => (ref.current.rotation.x += 0.01))
  // Return the view, these are regular Threejs elements expressed in JSX
  return (
    <mesh
      {...props}
      ref={ref}
      scale={clicked ? 1.5 : 1}
      onClick={(event) => click(!clicked)}
      onPointerOver={(event) => hover(true)}
      onPointerOut={(event) => hover(false)}>
      <boxGeometry args={[1, 1, 1]} />
      <meshStandardMaterial color={hovered ? 'hotpink' : 'orange'} />
    </mesh>
  )
}

<Canvas>
  <ambientLight intensity={0.5} />
  <spotLight position={[10, 10, 10]} angle={0.15} penumbra={1} />
  <pointLight position={[-10, -10, -10]} />
  <Box position={[-1.2, 0, 0]} />
  <Box position={[-1.2, 2, 0]} />
  <Box position={[1.2, 0, 0]} />
  <Box position={[4, 0, 0]} />
</Canvas>
\end{verbatim}

\begin{verbatim}
<div style={{textAlign: "center", fontStyle: "italic"}}>oh no</div>
\end{verbatim}

\noindent\rule{\textwidth}{0.5pt}

this is better because you dont even need to think about escaping. try,
see if can change muscle mem? \url{https://github.com/zhou13/vim-easyescape}

\noindent\rule{\textwidth}{0.5pt}

might be interesting: obsidian://show-plugin?id=obsidian-latex-suite
better than the current plugin?

\noindent\rule{\textwidth}{0.5pt}

super clean proof that \(1 = 0. \overline{999}\):
\[x = 0.\overline{999}\] \[10x = 9.\overline{999}\] \[9x = 9\] \[x = 1\]

\noindent\rule{\textwidth}{0.5pt}

\url{https://jeremykun.com} "math \(\cap\) programming"

\noindent\rule{\textwidth}{0.5pt}

sneak vim plugin \url{https://www.youtube.com/watch?v=HkY3LoQqKVA}

\noindent\rule{\textwidth}{0.5pt}

constructor theory? look into this later \#review

\noindent\rule{\textwidth}{0.5pt}

fatherly config plans: \url{https://topnotch.app}

\noindent\rule{\textwidth}{0.5pt}

\url{https://www.youtube.com/watch?v=Qnos8aApa9g} vim harpoon demo

\noindent\rule{\textwidth}{0.5pt}

\href{https://www.youtube.com/redirect?event=video\_description\&redir\_token=QUFFLUhqbWU5b05DZzZyX0syeGltbVAzSUZGWkFySTFEZ3xBQ3Jtc0tuX1VZUTFUcHFsaklnd2FFYnlFV1pseDU3Q1hxMm40aWcybXVtMGNkVXhrYWVQaThuY0E2dXJNR2dkVm1rZ3A3NkVTZ2pJWEhVblVDV0ZKcXdFdFZTdHA5b3V4aXExVWFRLXVpeVhtSlpnNDhBYjU5Yw\&q=https\%3A\%2F\%2Fwww.townscapergame.com\%2F}{https://www.townscapergame.com/}
\url{https://www.youtube.com/watch?v=0bcZb-SsnrA} wave function collapse maybe
with genetic algorythym?? human selection factor ray style land
construction?

\noindent\rule{\textwidth}{0.5pt}

"most of the time, you are stuck." - Sheldon Axler

\noindent\rule{\textwidth}{0.5pt}

huh, looks interesting. check this out later
\url{https://docs.helix-editor.com/keymap.html}

\noindent\rule{\textwidth}{0.5pt}

datum, being the singular form of data! this is why you say "these data"
instead of "this data"

\noindent\rule{\textwidth}{0.5pt}

\url{https://docs.google.com/document/d/1Dos29w-PMHbPD9ZFyTp\_8CkZP3e72KeR6VxetFOnRR4/edit}
category theory mahn doc

\noindent\rule{\textwidth}{0.5pt}

dil·et·tante

a person who cultivates an area of interest, such as the arts, without
real commitment or knowledge.

"a wealthy literary dilettante"

\noindent\rule{\textwidth}{0.5pt}

mahn, \url{https://github.com/starship/starship}

\noindent\rule{\textwidth}{0.5pt}

this is sick
\url{https://www.reddit.com/r/unixporn/comments/souv1t/bspwm\_i\_was\_told\_you\_guys\_would\_like\_my\_startup/}

\noindent\rule{\textwidth}{0.5pt}

"Categorical compositional distributional semantics, also known as
DisCoCat for short,"

\noindent\rule{\textwidth}{0.5pt}

quantum resources, from \href{https://thosgood.com}{tim!} -
\url{https://www.quantinuum.com} - \href{https://qubit.guide}{qubit.guide} -
\url{https://topos.site/topos-colloquium/} - ZX-calculus? like, pauli
matricies? - \url{https://graphicallinearalgebra.net} - we can have three
dimensional algebra?? - search for: diagramatic category theory, string
/ sheet diagrams - associahedron - tropical geometry?

\noindent\rule{\textwidth}{0.5pt}

intresting category theory reading from [cite/t:@nickm]
\url{https://drive.google.com/file/d/1lKQZ6dMxGTHZggNVbQG9JgGGbTo0QwZ6/view}
and also,
\url{https://drive.google.com/file/d/1lC7OeM7FTx7cVVv3ILijqwJVtugoEtVE/view}
\#readingsuggestion

\noindent\rule{\textwidth}{0.5pt}

\#name posit

\noindent\rule{\textwidth}{0.5pt}

\url{https://github.com/yoav-lavi/melody} this could make writing regex wayy
easier, check it out later!

\noindent\rule{\textwidth}{0.5pt}

gini coefficient is crazy elegant! super \#cool way of quantification

\noindent\rule{\textwidth}{0.5pt}

toon shaded mandlbulb!!! \url{https://youtu.be/h9NSV3Tj8Q8?t=34}
\href{KBxBlenderFractals.org}{KBxBlenderFractals} gotta try and
replicate.

\noindent\rule{\textwidth}{0.5pt}

this font is epic \url{https://dtinth.github.io/comic-mono-font/} use in tuts!
\#notcursed

\noindent\rule{\textwidth}{0.5pt}

one of the best units: grams/mile! \textasciitilde{}barak \emph{(for car emissions)}

\noindent\rule{\textwidth}{0.5pt}

helpful to change speed of media easily on multiple different sites
\texttt{js document.querySelector('video').playbackRate = 3}

\noindent\rule{\textwidth}{0.5pt}

got published in that journal one time\ldots{} figure out what it was and
update resume stuff also, add National ctf time team rank 59

\noindent\rule{\textwidth}{0.5pt}

to experiment with, when on windows:
\url{https://www.nvidia.com/en-us/studio/canvas/}

\noindent\rule{\textwidth}{0.5pt}

\#name ch!li like the pepper! figma design is
\href{https://www.figma.com/file/Z3qcCiUBVYOY8MZwlc6yS1/ch!li?node-id=0\%3A1}{here}

\noindent\rule{\textwidth}{0.5pt}

planck's constant is denoted as \(h\) because it was meant to be a
placeholder! so he called it, \texttt{holder}!

\noindent\rule{\textwidth}{0.5pt}

want to get this working: \url{https://github.com/Lorago/vfetch}
\url{https://github.com/Rosettea/bunnyfetch} \url{https://github.com/o2sh/onefetch}
\url{https://github.com/kiedtl/gfetch}

\noindent\rule{\textwidth}{0.5pt}

quantum mechanics, "I know everything about your car but unfortunately I
can't tell you anything about any of its parts."

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
dbg!(foo) // the superior way to print debug in rust.
// no more wack dedub traik prinln!-ing!
\end{verbatim}

\noindent\rule{\textwidth}{0.5pt}

better way to floor in js \texttt{js num | 0} turns out, \texttt{parseInt} sucks!
hint: try \texttt{parseInt(0.000000000002)}

\noindent\rule{\textwidth}{0.5pt}

reallly nice arch config:
\url{https://www.reddit.com/r/unixporn/comments/sh2lme/bspwm\_levuaska\_my\_attempt\_on\_making\_a\_color\_scheme/}

\noindent\rule{\textwidth}{0.5pt}

good article on
\href{mathematics/quantum/index.org}{mathematics/quantum/index} from
thomas rimer: \url{https://quantum.country/qcvc} check this out later!

\noindent\rule{\textwidth}{0.5pt}

ternary operators are epic.
\texttt{python \# python (falseValue, trueValue)[test]} the only thing is, this
evaluates both things\ldots{} instead, can use

\begin{verbatim}
a if x else b
\end{verbatim}

\noindent\rule{\textwidth}{0.5pt}

"don't become a monk in a monestary" - barry, referring to note taking

\noindent\rule{\textwidth}{0.5pt}

github has a quickswitcher! this is a gamechanger, thx
[cite/t:@zbuster05].

\noindent\rule{\textwidth}{0.5pt}

"classes of representation and how they move together" is what algebra
is! \textasciitilde{}-ted

\noindent\rule{\textwidth}{0.5pt}

\url{https://github.com/Exr0nProjects/obsidian-sage} yoooo?? [cite/t:@exr0n]
made a sick plugin! to try out.

\noindent\rule{\textwidth}{0.5pt}

\url{https://github.com/daaru00/obsidian-commander} could be interesting.
would love it to show the output below the block,
\url{https://forum.obsidian.md/t/new-plugin-sagecell/13364} style.

\noindent\rule{\textwidth}{0.5pt}

w/ darkreader, makes lots of ugly pages look nice

\begin{verbatim}
html {
  /* max-width: 111vh; */
  max-width: 78rem;
  padding: 3em 1em;
  margin: auto;
  line-height: 1.75;
  font-size: 1rem;
}
\end{verbatim}

modified from \url{https://www.swyx.io/css-100-bytes/}

\noindent\rule{\textwidth}{0.5pt}

python infix operators? this is sick.
\url{http://tomerfiliba.com/blog/Infix-Operators/} essentially, of
\texttt{add(add(add(5,6),7),8)...} we can write \texttt{py 5 |add| 6} with a bit of
trickery.

\noindent\rule{\textwidth}{0.5pt}

\url{https://www.yourdictionary.com/equivalate} is a word! this is amazing.

\noindent\rule{\textwidth}{0.5pt}

\#name vacuo

\noindent\rule{\textwidth}{0.5pt}

"the game I play is a very interesting one: it's imagination in a tight
straight-jacket" - feynman

\noindent\rule{\textwidth}{0.5pt}

\#name ilk

\noindent\rule{\textwidth}{0.5pt}

abstract math is "like a metaphor" - ted

\noindent\rule{\textwidth}{0.5pt}

\url{https://www.patreon.com/posts/52586182?scrlybrkr=6e7abbc0} \#cool blender
stuff \url{https://www.youtube.com/watch?v=NmZxWXeIjJI}

\noindent\rule{\textwidth}{0.5pt}

\#stack to finish: \url{https://youtu.be/mTz0GXj8NN0?t=1418}

\noindent\rule{\textwidth}{0.5pt}

vim in browser, to try \url{https://github.com/glacambre/firenvim} yo.
\url{https://github.com/gelguy/wilder.nvim}
\url{https://github.com/machakann/vim-sandwich} could be interesting:
\url{https://github.com/hrsh7th/nvim-cmp}
\url{https://github.com/akinsho/bufferline.nvim}

\noindent\rule{\textwidth}{0.5pt}

\#cool chrome extension,
\url{https://chrome.google.com/webstore/detail/draft-by-slite/ljkidlijlaapmiilabpldhmhekeionfh?hl=en}
super easy capture

\noindent\rule{\textwidth}{0.5pt}

\begin{quote}
"Like gods, these mathematical models were opaque, their workings
invisible to all but the highest priests in their domain:
mathematicians and computer scientists." (Cathy O'Neil)
\end{quote}

\noindent\rule{\textwidth}{0.5pt}

\#name lohah

\noindent\rule{\textwidth}{0.5pt}

super \#cool artwork utilizing noise-based volume displacement
\url{https://leegriggs.com/volume-mesh} can't really be done easily in
blender.. tried here \href{KBxBlenderFractals.org}{KBxBlenderFractals}

\noindent\rule{\textwidth}{0.5pt}

procedurally generate language from arrival

\noindent\rule{\textwidth}{0.5pt}

super \#cool things made with curl noise and flow fields!

\noindent\rule{\textwidth}{0.5pt}

\#cool lisp interpreter in conways game of life
\url{https://github.com/woodrush/lisp-in-life}

\noindent\rule{\textwidth}{0.5pt}

look into this working /w taproot:
obsidian://show-plugin?id=obsidian-icons-plugin

\noindent\rule{\textwidth}{0.5pt}

this is crazy \#cool,
\url{https://www.youtube.com/watch?v=-th6w\_ZIvpA\&ab\_channel=BenThroop}

\noindent\rule{\textwidth}{0.5pt}

\#name for something: etude. means, a peice of music for the point of
demonstration.

\noindent\rule{\textwidth}{0.5pt}

\#cool word: grok. to understand something intuitively $\backslash$ truly

\noindent\rule{\textwidth}{0.5pt}

could be a \#name for smt: azimuth

\noindent\rule{\textwidth}{0.5pt}

\href{https://www.youtube.com/watch?v=uvap4gEOC5I\&ab\_channel=SonyPicturesHomeEntertainment}{very
good scoring in this scene. use for later}

\noindent\rule{\textwidth}{0.5pt}

\section{moonshot}
\label{sec:orgd59f3c9}
Google X Moonshot. Dream job?

\noindent\rule{\textwidth}{0.5pt}

surreal numbering system: completely ordered class of the reals and the
infinite and infinitesamal, coined by knuth and proven using conways
game of life and combinatorial game theory! \#cool

\noindent\rule{\textwidth}{0.5pt}

\#cool word: beleaguered!

\noindent\rule{\textwidth}{0.5pt}

atlas by bicep: sick music video, would love to replicate the effect.

\noindent\rule{\textwidth}{0.5pt}

quick proj idea: GAN to generate kanji! dataset, here:
\url{https://www.kaggle.com/nmamdbts/yumincho-kanji}

\noindent\rule{\textwidth}{0.5pt}

predictability horizon! \#cool concept

\noindent\rule{\textwidth}{0.5pt}

would love to buy some silicon, either
\href{https://www.amazon.com/Silicon-Metal-99-999-Pure/dp/B08FVLJM8L}{this}
or
\href{https://www.amazon.com/Silicon-Wafer-Single-Sided-Polish/dp/B08RZ5ZYNF/}{this.}

\noindent\rule{\textwidth}{0.5pt}

config! \url{https://github.com/sainnhe/tmux-fzf}

\noindent\rule{\textwidth}{0.5pt}

\href{https://ncatlab.org/nlab/show/category+theory}{category theory}. to
\#review \href{KBxSystemsofSystemsinNatureandDeepLearning\#category theory.org}{KBxSystemsofSystemsinNatureandDeepLearning\#category theory}

\noindent\rule{\textwidth}{0.5pt}

read this later! supposed to be generalization of godel's incompleteness
theorem \url{https://ncatlab.org/nlab/show/Lawvere\%27s+fixed+point+theorem}

\noindent\rule{\textwidth}{0.5pt}

proximal: possible \#name! distal: also a good \#name?

\noindent\rule{\textwidth}{0.5pt}

mechanical pencils! want to get:
\url{https://www.amazon.com/Al-Star-Graphite-Mechanical-Pencil-L126/dp/B000FA5EHO/ref=sr\_1\_1?crid=1AGSNPXV81ZUF\&dchild=1\&keywords=lamy+mechanical+pencil\&qid=1633903922\&s=office-products\&sprefix=lamy+mechan\%2Coffice-products\%2C232\&sr=1-1}
or,
\url{https://www.amazon.com/Mechanical-Pencil-Roulette-Silver-M510171P-26/dp/B004OHNTVC/ref=sr\_1\_3?dchild=1\&keywords=kuru\%2Btoga\&qid=1633903910\&s=office-products\&sr=1-3\&th=1}
maybe
\url{https://www.amazon.com/Black-Lacquer-Mechanical-Pencil-Scriveiner/dp/B08BZQDYT7/ref=sr\_1\_3?dchild=1\&keywords=luxury+mechanical+pencils\&qid=1633903451\&sr=8-3}

\noindent\rule{\textwidth}{0.5pt}

dismaland: besument park. by banksy. check it out.

\noindent\rule{\textwidth}{0.5pt}

Vox Populi: the beliefes of the majority

\noindent\rule{\textwidth}{0.5pt}

simplex: simplileft geometric shape in a given dimension? \#cool concept

\noindent\rule{\textwidth}{0.5pt}

eom: good \#name for something. means: end of sentence but it sounds
cool!

\noindent\rule{\textwidth}{0.5pt}

defining new term: gardening, as the term for knowledge organization.

\noindent\rule{\textwidth}{0.5pt}

explanation of power of emergent property: "that even when the
underlying rules for a system are extremely simple, the behavior of the
system as a whole can be essentially arbitrarily rich and complex."
\textasciitilde{}wolfram
\href{https://www.wolframscience.com/nks/p737--computational-irreducibility/}{computational
irreducibility}

\noindent\rule{\textwidth}{0.5pt}

hypergraph! edges are sets of points not connections. one model for
etomolgysarus or, bipartite with roots and words or, store as one and
represent subset as another.

bfs and look for number of shared.. roots? plug in for force

\noindent\rule{\textwidth}{0.5pt}

graph theory! i wanna take it. \textasciitilde{}"most likely will exist next year"
\textasciitilde{}exr0n

\noindent\rule{\textwidth}{0.5pt}

\#cool \#name: orhac

\noindent\rule{\textwidth}{0.5pt}

analog, as something that is analogous

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
<div style="border: 1px solid red, width: 200px, height: 200px, background-color: red"> testing a div?? </div>
\end{verbatim}

\noindent\rule{\textwidth}{0.5pt}

\url{https://jasonwarta.github.io/latex-matrix/} is very useful

\noindent\rule{\textwidth}{0.5pt}

lemma sort is \#cool!

\noindent\rule{\textwidth}{0.5pt}

convecto, \#name for smt means gather in latin

\noindent\rule{\textwidth}{0.5pt}

\begin{itemize}
\item shopping list:
\begin{itemize}
\item phone case:
\begin{itemize}
\item \url{https://rhinoshield.io/pages/solidsuit?device=iphone-12-pro}
\end{itemize}
\item glasses cleaning cloth
\begin{itemize}
\item \url{https://www.amazon.com/MagicFiber-Microfiber-Cleaning-Cloths-PACK/dp/B0050R67U0}
\end{itemize}
\item card holder
\begin{itemize}
\item \url{https://www.amazon.com/Carbon-Blocking-Minimalist-Aluminum-Version/dp/B07C1N6L2D/ref=sr\_1\_24?dchild=1\&keywords=thin+card+holder\&qid=1631938390\&sr=8-24}
\end{itemize}
\item desk pad
\begin{itemize}
\item \url{https://www.amazon.com/Glorious-PC-Gaming-Race-G-XXL/dp/B07C84TQ74/ref=sr\_1\_21?dchild=1\&keywords=extra\%2Blarge\%2Bcloth\%2Bdesk\%2Bmat\&qid=1631940333\&sr=8-21\&th=1}
\end{itemize}
\item screen protector
\begin{itemize}
\item \url{https://www.amazon.com/Mkeke-Compatible-12-Protector-Pro/dp/B08CV2B3DC}
\end{itemize}
\end{itemize}
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

\#name for someting: taba

\noindent\rule{\textwidth}{0.5pt}

realized, intrested in the concept of granularity

\noindent\rule{\textwidth}{0.5pt}

this is another note

\noindent\rule{\textwidth}{0.5pt}

new note

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
CodeMirror.Vim.map('jf', '<Esc>', 'insert')
CodeMirror.Vim.map('j', 'gj', 'normal')
CodeMirror.Vim.map('k', 'gk', 'normal')
\end{verbatim}

\noindent\rule{\textwidth}{0.5pt}
\end{document}
