% Created 2021-09-11 Sat 16:41
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\date{\today}
\title{Water beads experiement}
\hypersetup{
 pdfauthor={},
 pdftitle={Water beads experiement},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Water beads experiment}
\label{sec:org90f39d2}
\href{https://docs.google.com/presentation/d/1YWt7acmZWPU3U4ZgJEKJtsHT3Pke3RUBJiUB0qJxZ44/edit?pli=1\#slide=id.g981892b000\_0\_5}{Link} -
Sugar types - Sucrose is a disaccharide - one glucose and one fructose -
cane sugar is a disaccharide - C₁₂H₂₂O₁₁ - Summarize observational
data - Beads shrivel in all except water and sugar - Change in water is
minimal - Hypothesis - Sugar bonds to each other and does dehydration
synthesis? therefore more water - Therefore water goes into the beads? -
Polarity of molecules? - Interacting charges pull water out of the
bead? - Something else went into the bead? - Things that would be
helpful - What is the concentration of the water in the beads? - Super
absorbent polymer: sodium polyacrylate - negatively charged sodium -
What is the actual concentration of sugar? 75g water meaning 75g total
solution? \# My Food Data - Just said 46/50 g protein and figured out a
diet - Looked up ideal diet for fifteen year old - Protein RDIs were by
weight, is it really scalar like that?

\section{Problem set + final deliverable}
\label{sec:orgfcf0bd3}
\url{https://docs.google.com/document/d/1teJ0qt5p0ls0bKx1dIo6nEvqR1wITbAQZcjUkEG45Wo/edit}

\noindent\rule{\textwidth}{0.5pt}
\end{document}
