% Created 2021-09-11 Sat 16:40
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Cell Cycle Regulation}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Cell Cycle Regulation},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Cell Cycle Regulation}
\label{sec:org8f3de8a}
The Problem: \textbf{Cells need to know whence to divide itself.}

\subsection{Cell Cycle Regulators}
\label{sec:org61cb3dd}
\subsubsection{Drivers}
\label{sec:orga5539ec}
=> Drivers tell cells when to divide. The processes that move a cell
forward through its life are called "drivers".

Drivers consists of two parts: a switch + a cyclin. A "switch" ---
informed by environmental factors and checkpoints (see below) --- turns
on a "cyclin" protein this cyclin protein actually drive cell forward.

\subsubsection{Checkpoints regulate drivers' actions}
\label{sec:orgcd1ffa4}
Should the cells not meet the requirements of a checkpoint, its driver
would be stopped; and/or it will be called to self-destruct.

There are two main types of regulators:

\textbf{Positive Regulators} push the cell cycle forward, CDK, upon lots of
cycling binding to it and the meeting of checkpoint.

\textbf{Negative Regulators} hold the cell cycle back due to a response to a
checkpoint or an environmental factor

Here are some common checkpoints:

\begin{itemize}
\item \textbf{G1/S Checkpoint} (After S) --- external factors and growth factors
(nutrients, raw material, DNA damage) , along with measurements of the
volume, shape of the cell and the duplicated DNA, ensure that the
pre-G2 cell is intact and healthy before moving onto G2
\item \textbf{Inter s-checkpoint} (During S) --- during S, check for DNA damage.
\item \textbf{G2/M Checkpoint} (After G2) --- before mitosis, check that the cell
has correctly duplicated parts and tools needed for replication
\item \textbf{Spindle Checkpoint} --- checking for the attachment of all
kineticores to the spindles such that all the chromasomes could be
correctly lined up and seperated later
\end{itemize}

Growth Factors that the cells measure: the 1) Size of the cell 2) the
nutritional state of the cell.
\end{document}
