% Created 2021-09-27 Mon 12:02
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\begin{center}
\begin{tabular}{l}
title: ML Day One\\
course: ML301\\
author: Huxley Marvit\\
source: \href{KBML\_Master\_Index.org}{KBML\textsubscript{Master}\textsubscript{Index}}\\
\end{tabular}
\end{center}

\noindent\rule{\textwidth}{0.5pt}

\section{Course Expectations}
\label{sec:org7e06ca1}
\begin{itemize}
\item Hf, work with Wes to find interesting projects
\item Be supportive, yatta yatta
\item Make your own learning decisions

\begin{itemize}
\item Figure out how you learn
\item eg. if you don't learn well with presentations, you don't have to
listen.
\end{itemize}

\item Assignments are individual. \texttt{=cite your sources!=} working with
classmates is okay, but you need to cite them.\\
> "School is supposed to be stressful" \emph{Wes Chao, 2020}
\end{itemize}

\subsection{What is Machine learning?}
\label{sec:orgedd0a63}
My answer: Algorithms which learn from experience.

\begin{quote}
Almost always involves large amounts of data. The more data the
better.
\end{quote}

Expensive to process - focus on the simplest way to get a \emph{decent}
answer

\subsection{Ethics}
\label{sec:org271b235}
How did we get the data? Do the people we got that data from consent?

Algo = thing we use to process data Model = thing we get at the end.
Algo + plus weights \texttt{Algo !} Model=
\end{document}
