% Created 2021-09-27 Mon 12:02
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Validation}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Validation},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\noindent\rule{\textwidth}{0.5pt}

\section{Validation}
\label{sec:org6622bc7}
We have visualized out models and used human judgment to, well, judge
them. We have \emph{not} done this algorithmically or mathematically.

\subsection{Why?}
\label{sec:orgf3e1f90}
Some things are blind to the human eye. Eg. underfitting and
overfitting.

Not enough data, the algorithm was buggy (can't we see these though?
maybe just not as easily?)

\subsubsection{Underfitting}
\label{sec:org34bcc2b}
Wrong algorithm, buggy, or the data just sucks / there isn't actually a
correlation.

\subsubsection{Overfitting}
\label{sec:org950a6e6}
Training \emph{to well} to our dateset, making it not applicable to the real
world / other data.

\subsection{Bias-Variance Tradeoff}
\label{sec:org75f9e45}
Bias - off Variance - inconsistent

We want low bias low variance (doih).

\subsection{Holdout? nah, let's cross validate!}
\label{sec:org9c7f2c8}
Like holdout, but you do it multiple times with different chunks of data
'held out'

\subsection{Validation?}
\label{sec:orge112c23}
What do? - Accuracy - Easy, but not super effective / informative. -
Precision, Recall, F-measure - True positive, false negative, and all
the permutations. - Precision = \(\frac{TP}{TP+FP}\) - Recall
\end{document}
