% Created 2021-09-12 Sun 22:48
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{WWI Strategies}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={WWI Strategies},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{WWI Strategies}
\label{sec:orge73b5bc}
German's war plan (The Schlieffen Plan): rely on the railway to fight
upon two fronts. First, rapidly defeat the French in a cyclic fashion;
then, shuttle individuals to the slower Russian front.

When implementing part 1 of the plan, the Germans were took by surprise
when the Russians pushed into Germany. Furthermore, the French later
quickly got reinforcements from England. While German communication was
cut off intermittantly, the French and English conversatinos were
uninterrupted. Because of the machine gun, which made foot soilders kind
of useless, the war turned into a stalemate with no one being able to
advance. The germans tried to take Russia; they killed a lot of people,
but no hope was given up. The English/French tried to take Turkey, lots
of people died, but still nothing.

\begin{itemize}
\item General Pétain had to fight and defend the Verdun area with minimum
resources; both German and French armies suffered great casulties, but
eventually the Germans gave up.
\item The Allied offensive tried to use a stupid amount of weaponary and
people to move through the front, however, it was to very little gain.
\item The allies did not observe the international rules preventing
noncontraband imports for countries at war; hence, they slowly
abolished the economic rules and leveraged this to create a naval
blocade to starve german economy.
\item The US tried to protest this, because they did business with Germany;
however, when the US entered the war on behalf of the Allies, they
ditched that and enforced the same regulatinos.
\item The Germans, citing the English abuse of naval law, started
torpeedoing anything they see next to English waters with a submarine.
\item Once a British ship was torpeedoed by Germany, 118 American lives were
lost.
\item Woodrow Wilson threatened that another such act would be reconized as
"deliberately unfriendly" behavior by the Germans, which caused them
to stop torpeedoing by much for 2 years.
\item The Germans threw a lot of resources on naval fighting in hopes of
preventing the blocade from starving them. Although they took out a
lot of British men, they did not successfully undermind the British
sea dominance.
\item Against the will of most italians, the Allies secretly bought the
support of Italy by promising them land and larger colonies.
\item The Germans equally tried to stir the nationalistic ideals of poland
and ukraine and Ireland and bought the sultan to proclaim holy war.
Nothing amounted to much.
\item The German Zimmermann telegram tried to leverage Mexico as a line of
defense against the United States --- that if the US attacked germany,
Mexico would attack the US. This shocked US public opionion.
\item Instead of appealing to route nationalism, allies appealed to
nationalistic discontent.
\item Appealing to the Jews and the Armenians, the British government
dragged them into the conflict and disrupted the ottoman empire.
\item The allies then took German colonies.
\item Allied with the British, Japan also forced China to make a series of
consessions that protected the Nortern China region from the Germans.
\item Woodrow wilson, although personally allied with England and France,
kept out of the war and tried to bring peace without a victory.
\item CLAIM: Russia was the first victim in the war. The troops mutinied and
the government abdicated to create a provisional russian goverment.
\end{itemize}
\end{document}
