% Created 2021-09-27 Mon 12:01
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Kenedy, Chapter 1}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Kenedy, Chapter 1},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents



\section{Kennedy, Chapter1}
\label{sec:org0638420}
\subsection{Situations with Europe, pre 1500}
\label{sec:orgf3246c9}
\begin{quote}
1500, the date chosen \ldots{} to mark the divide between modern and
pre-modern times.
\end{quote}

See \href{KBhHIST201Europe1500s.org}{KBhHIST201Europe1500s}

\subsection{The Early Global Players}
\label{sec:orgb7af3e4}
Although it was not evident to see Europe's boom in the 1500 in, well,
the 1500, there were definitely great centres of tho world at the time.

\begin{quote}
Before investigating the causes of [European] rise, it is necessary to
examine the strengths and the weaknesses of the other contenders.
\end{quote}

\subsubsection{Ming China}
\label{sec:org89ccff7}
ADVANCED in tech. ADVANCED in structure. SUPERIOR in culture: Ming China
was extremely technologically advanced and culturally strong. It was the
biggest state + economy in Asia.

See \href{KBhHIST201MingChina1500.org}{KBhHIST201MingChina1500}

\subsubsection{The Ottomans}
\label{sec:orgdf90d17}
When China was failing, the Ottomans grow w/ Muslimdom --- Ottomans were
the largest muslim nation in Europe + a serious threat to Christendom.

See \href{KBhHIST201Ottomans1500.org}{KBhHIST201Ottomans1500}

\subsection{The Europeans' Rise}
\label{sec:org43bf18b}
Guiding question: so, how did scattered Europeans become the number 1
world player from futal tribes?

See \href{KBhHIST201RiseOfEurope1500.org}{KBhHIST201RiseOfEurope1500}

Based on the \href{KBhHIST201HistModHist.org}{KBhHIST201HistModHist}
Models of History Systems, there are two theories under which Kennedy's
analysis could be evaluated.

\begin{itemize}
\item Kennedy deux. Arrigi

\begin{itemize}
\item War as a form of trade strength
\item Europe lead the world to transformation from territorialist to
capitalist model
\end{itemize}

\item Kennedy deux. Predatory Theory

\begin{itemize}
\item War as an end in and of itself
\item Growth in expansion correlated to success with mil. tech.
\end{itemize}

\item Growth through Exploitation
\item Protestant Work Ethic
\item Geol, Geog, Luck
\end{itemize}

\subsection{Why Kennedy is Frustrating}
\label{sec:orge32165e}
Kennedy's arguments is very frustrating.

\href{KBhHIST201KennedyIsFrustrating.org}{KBhHIST201KennedyIsFrustrating}
\end{document}
