% Created 2021-09-12 Sun 22:48
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Mason Chapter 8}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Mason Chapter 8},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Mason, Ch 8}
\label{sec:org2691dcd}
\#flo \#disorganized

=> Imperialism: advanced contry control weak one

\begin{itemize}
\item Imperialism: driven by compettion + diplomacy.

\item Europeans had massive land control at the height of imperialism.

\item But! Imperialism was short; African nationalism sprung up quickly.
\end{itemize}

\subsection{Rise of Imperialism}
\label{sec:org9fd572b}
\textbf{CLAIM: Reasons for african scramble: national pride, stsrategic
competition, new markets, raw material, and labor!} => Used colonies as
effective tax-evasion zones free of tariffs

\begin{itemize}
\item European depression from 1873-1890 became the drive for overseas
imperialistic ventures.

\item Also, Europeans felt taking over other countries is also humanitarian.

\item Self-imposed tariffs lead to “economic protectionism, which furthered
the decline in trade

\item Thayer Mahan recognized the importance of having a navy to
colonization (Big Brit Navy => Big Brit Colony); so, Amercia and
Germany beefed up tehir navy and began a series of naval-based
conquests.

\item \textbf{Social darwinism}: the survival of the fittest applies to natinos ---
hence advocates for imperilasm

\item Spread of imperialism began from spain => French => dutch => England.

\item communists claimed that imperialism is the natural consiquence of
capitalism

\item First to colonize is the first to rebel. Case and point: Amercia.
\end{itemize}

\subsubsection{The History}
\label{sec:org41dd9a3}
\begin{itemize}
\item Africa was largely unexplored before the 19th century --- before,
africa was only "expoited" by means of slave trade.
\item Construction of the Suez canal created a boom in shipping.
\item Belgian king Leopold's assigment of journalist Henry Stanley
established the Congo Free State.
\item Alarmed, other nations joined in and established guidelines for how to
divide the continent into effective sizes.
\item 2 countries spared from the scramble: Ethiopia, a native empire, and
Liberia: a colony for freed american slaves.
\item the dutch Boers and the british fought over who cotrolled South Africa
and surrounding diamond mines. Eventually, the brits won.
\end{itemize}

\subsection{Asia}
\label{sec:orge082c92}
\begin{itemize}
\item Britian Asian colonization: India! Rich source of manpower and
resources.
\item The French took Vietnam, but strong nationalism drove them out in the
1950s.
\item Pressure from all fronts lead china to establish interlocking treaties
that gave europeans de facto control to key trade regions. => CLAIM:
this eventually lead to the death of China, the Empire
\end{itemize}

\subsection{Models and Results of Imperialism}
\label{sec:org4878c50}
\begin{itemize}
\item European colonizations usually started with Nationally chartered
exploratory companies (think: BEIC); evenutally, goverments take over.
\item through imperialism, European culture became the dominant viewpoint in
much of the southern hemisphere.
\item Cities show up, and so did production of cash crops + a cash economy.
\item European education stimulated literacy.
\item European colonization created weak governments when independence
finally was achieved.
\item Direct effect of imperialism: land holdings and timezones.
\item After the rapid de-colonization in the 20th century, the Third World
was established and CLAIM: was pivital during the cold war.
\item European thinking lead to European nationalist ideals, which CLAIM:
contributed to the downfall of European colonies.
\end{itemize}

\subsection{CN11302020}
\label{sec:orgbe7698b}
\#flo

\begin{itemize}
\item About the \textbf{scramble for Africa} and the imperialist movement
\item Today: all of Imperialism!
\item The Scramble for Africa, w.r..t the congo

\begin{itemize}
\item Hand Cutting! A mechnasism to meet the quota of cartridge use and as
a a mechanism of defense
\end{itemize}

\item IR Caused science and tech advancements

\begin{itemize}
\item Steel + the steam engine => the core driver of technology - Think!
The Effel tower: the celebration of the 1889 world's fair to create
a celebration of steel
\item The telegraph --- communication across continents => Post office
would be delivered as part of the mail
\item Standardized oil and the natural rubber
\item 1870s-1876 --- electricity and the telephone: enabled real-time
communication
\item 1884 --- Standardization of time, and created the official prime
meridian at Greenwitch
\item American timezones was messy and city-based, which was later
standardized
\item Rhodisia

\begin{itemize}
\item Connected telegraph between two different regions --- cape town to
chairo
\end{itemize}

\item Archeology/Paleotogy/Museums/Science

\begin{itemize}
\item 1812 --- establishment of the Elgin marbles from Greece
\item 1829 --- Institute for Archeologoical Correspodence: create the
basis of first organized science
\item 1830 --- Establishment and justification of racial divide w.r.t.
"self study" and "scientific exploration"
\item 1859 --- Darwin (about here is where scientific racism started,
ala "development of men")
\item 1898 --- cell theory
\item 1840 --- dinasoures!
\item 1864 --- establishment of the concept of the Eugenics and the
process of forced sterialization
\item 1869 --- the Periodic tables
\end{itemize}
\end{itemize}
\end{itemize}

"The White-Man's Burden" --- the idea that the white man is racially
superior and should go into the "less developed" region and bring the
people into civilization
\end{document}
