% Created 2021-09-12 Sun 22:48
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Ml Self Eval}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Ml Self Eval},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#ret

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
If you want to get a head start on your self evaluation before it is available on the school website, here are the questions.

Please write 1-2 sentences per question, or as much as you need to answer the question.

Do not write your answers in the school website! If you reload the page by accident, your work is gone. Write them in Docs or Word or your favorite text editor and then copy them in.
\end{verbatim}

Questions - Share an example of a difficult problem you solved in one of
your projects. - A difficult problem for me that I 'solved' was the very
last problem in the Neural Networks assignment: making the model perform
better. While sounding simple enough, the process I went about doing
this was essentially guess and check; it was a type of computer science
problem that was almost entirely new to me. In fact, I don't know if it
can quite be considered a science yet --- perhaps this is what the
transition stage from an 'art' to a 'science' looks like?

\begin{itemize}
\item Of the concepts we discussed, which one(s) did you find most
interesting or useful, and why?

\begin{itemize}
\item More broadly speaking, a concept that we have discussed in proxy is
the sheer power and beauty of emergent properties. One of the
reasons that makes ML so interesting and so unique (at least to me)
is that it deals with harnessing this power of emergent property to
form a type of intelligence.
\end{itemize}

\item What concepts did you find most challenging, and why?

\begin{itemize}
\item Convolution Neural Networks confused me quite a bit, as I didn't
have a strong understanding of how basic Neural Networks worked
going in. This made me miss the importance of the differences of a
CNN; after the fact, I now have an altered outlook on how I should
approach learning about specialized topics.
\end{itemize}

\item What are some ways that you displayed good habits of mind or
contributed to a good learning environment in the class?

\begin{itemize}
\item I am genuinely interested in ML. I spent a lot of my time working
with a good friend; my belief is that approaching learning this way
will naturally lead to good habits of mind.
\end{itemize}

\item What was the most useful or memorable piece of feedback you received
this semester, and how did you act on it?

\begin{itemize}
\item One of the most memorable pieces of feedback was this: "However, the
exercise isn't merely a coding exercise --- it's also to answer the
question." I coudn't belief that I had gotten so caught up in the
code that I missed the point of the question! --- It was a good
reminder to step back and untangle myself from the weeds every once
in a while.
\end{itemize}
\end{itemize}
\end{document}
