% Created 2021-09-27 Mon 12:00
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Fascism. Time.}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Fascism. Time.},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\#flo \#ref \#disorganized \#incomplete

\noindent\rule{\textwidth}{0.5pt}

\section{No, your the one who's actually fascist!}
\label{sec:org0dfb577}
paris peace settlments marked the end of the war,

many european governments went into isolationaism, neutrality, or
pasifism

created the leuge of nations

lots of unrest and economic instability, poverty, ect

hitler rose to power using this

usa teamed with the ssoviet union? to end nazi germany, then after the
wwar it turned into distrust and rivary and the cold war

germany had a bunch of treaties, coudnt pay stuff, ended up hyper
inflating.

american depressing hit, worldwide impacts, germany got hit especially
hard, demagogue time!

musolinni made fascism? believed in economic security and law and order,
even if done through dictatorship

hitler did stuff like musssolina, wiggled his way into power, ect.

except he did it in three months, not three years.

hitler did alot of dictatorhsip stuff

wasnt a control freak like stalin.

\begin{quote}
he missed meetin gs, worked irr egu lar hour s, and was often
disorganized. Hitl er valu ed pers on al loyalty far more than
efficiency.
\end{quote}
\end{document}
