% Created 2021-09-11 Sat 09:36
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Ethics Questions}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Ethics Questions},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Berdanido}
\label{sec:orgc21735a}
\begin{enumerate}
\item What are the ethical choices people faced? What, if any, actions
would you consider unethical? Why? The FBI and teams at Apple had to
face the choices whether to push an OTA update to the phone of the
San Bernadino Shooter. When Apple failed to do so, FBI attempted to
use a third-party service that decrypted the device. Because of the
court-issued injunction, the FBI was acting within its legal capacity
to do so. However, Apple made the difficult moral decision in not
co-operating with the FBI with their investigation. Although I don't
believe that they were fully in their legal rights to do so, I \emph{do}
believe their actions were ethical. They did not divert the resources
to build a back-door to their devices that could be issued via an OTA
update, which therefore protect future customers from attack.

\item What, if any, actions in this story do you think should be illegal?
What actions are actually illegal? Specify laws that might be
relevant, even if no one was caught or prosecuted. Digital locks, if
breakable, could be done. The FBI was in their rights to issue an
injunction, but they should also attempt to seek third-party help
should they want to break the encryption. For instance, a lock maker
is not responsible to issue a master key to their lock when the FBI
could simply break the door.

\item What things do you think the people involved could have done to
achieve their goals while staying within legal and ethical bounds? I
believe that the FBI acted reasonably here: seeking a third-party
security official to attempt to acquire the decryption key. However,
Apple should therefore strengthen their security, as that act would
protect against future attacks by third-parties down the line.

\item What would you consider appropriate punishment? If relevant to your
story, how does that compare to the punishments that were handed
down? There is no punishment that could be issued here. I believe
that Apple's refusal, although perhaps in-lawful, would be a civil
and not criminal case. As per aforementioned, though, they should
attempt to increase the security of their devices in order prevent
future parties from breaking into their systems.

\item What are the technical lessons that can be learned to improve
security? I believe that the security company leveraged three
zero-days to be able to trigger the decryption mechanism on iPhone
unlock to bring down full-disk encryption. Because of the fact that
newer iPhones have e-SIMs, I think it is no longer possible to
leverage the iMessage bug to introduce the first payload. Also, I
believe that iMessages are now encrypted now until phone unlock,
instead of at the moment they were received: protecting against this
exploit.
\end{enumerate}

\section{Silk Road}
\label{sec:orgf1b7b7f}
\begin{enumerate}
\item What are the ethical choices people faced? What, if any, actions
would you consider unethical? Why? "Force" (Nob) leveraged going
under undercover to trick individuals to flip for the DEA. I don't
necessarily believe that this act is \emph{ethical}, but it I nevertheless
don't believe that he could have done anything different given his
job as an DEA agent.

\item What, if any, actions in this story do you think should be illegal?
What actions are actually illegal? Specify laws that might be
relevant, even if no one was caught or prosecuted. I think the
process of working in this is definitely de-jure not illegal, because
of the fact that there is no laws that would prevent a DEA/FBI agent
from simply doing their proper job. However, I do believe that parts
of staging an undercover investigation is quite strange as a behavior
and should be formally investigated for their legality as it
nevertheless may trick/put innocent people into crime or otherwise
exasperate the extent of the crime.

\item What things do you think the people involved could have done to
achieve their goals while staying within legal and ethical bounds? I
believe that the legal bounds were met. However, the bounds of ethics
is harder to meet here because what they do essentially has to
include some ethically challenging areas. One potential route may
include seeking stronger security systems and attempting to passively
observe and indite the actions instead of attempting to trick those
into action.

\item What would you consider appropriate punishment? If relevant to your
story, how does that compare to the punishments that were handed
down? The punishment is likely appropriate as handed down: double
life sentence. However, due to the designation of the owner of the
website as a "kingpin", he is being held in a maximum security prison
through it is likely that he had much lower flight risk than others
in a similar position.

\item What are the technical lessons that can be learned to improve
security? Attempt to segregate usernames! It seems like the arrest
and breakthrough came when his username was digitally linked with
that of another which eventually lead to a much earlier fourm post
that contained his email. This was not a breach that needed anything
but social engineering, which is something that eventually the
creator of this site fell to.
\end{enumerate}
\end{document}
