% Created 2021-09-27 Mon 12:02
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Som With A Perspective}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Som With A Perspective},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\#ret

\noindent\rule{\textwidth}{0.5pt}

\section{My Shaggy Dog Story}
\label{sec:org39f520f}
I used to own a dog that was uncommonly shaggy. Many people remarked
upon its considerable shagginess. They would say things like, "man, that
dog is really shaggy," or "I've never seen a dog so shaggy." One time,
on a walk, a lady said to me, "that dog is quite uncommonly shaggy." I
continued for a while with my shaggy dog, getting remarks on its
shagginess. After all, it was uncommonly shaggy. However, it all changed
when I learned that there are contests for shaggy dogs. So, of course, I
entered my dog. The dog won first prize for shagginess in both the local
and the regional competitions. I continued entering my dog in shaggy dog
competitions and my shaggy dog kept winning them. One time, a judge,
after the competition, remarked once again on the uncommon shagginess of
my dog. He then offered to buy my shaggy dog from me. I, of course,
given how shaggy my dog was, declined. I then entered the dog in
ever-larger contests, until finally I entered it in the world
championship for shaggy dogs. This competition was the cream of the crop
when it came to shaggy dogs. It finally came to the time of competition.
The judges brought me and my shaggy dog in, and when the judges had
inspected all of the competing dogs, they remarked about my dog. They
said, "He's not that shaggy."

This is Huxley, and my shaggy dog, with a perspective.

Stylistically inspired by the works of Ted Cohen.
\end{document}
