% Created 2021-09-11 Sat 08:17
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\begin{center}
\begin{tabular}{l}
title: The I is Never Alone English Reading Notes\\
course: ENG201\\
author: Huxley Marvit\\
source: \href{00-Topic-KB20200825141900.org}{00-Topic-KB20200825141900}\\
\end{tabular}
\end{center}

\noindent\rule{\textwidth}{0.5pt}

\href{KBhENG201TheIIsNeverAlone.org}{KBhENG201TheIIsNeverAlone} Jack's
Take \href{KB2NotesonTheIIsNeverAlone.org}{KB2NotesonTheIIsNeverAlone}
Exr0n's take

\texttt{=Mirrors=} reflection - same with the parrots? \#why

\begin{quote}
the depth of his solitude
\end{quote}

Captures parrots, lets them struggle

Trains parrots while feeding seeds (reward training)

\begin{quote}
by instructing one another, soon all the parrots on the isle were
repeating Siriak's name from dawn to dusk
\end{quote}

Colonization? Culture spread / destruction..?

\begin{quote}
In spite of the continual presence of his self which he was confined
to by solitude, he struggled to remember that he also existed outside
of himself.
\end{quote}

Cannot escape himself due to his solitude Confined to his point of view?
Lacks empathy because nothing to have empathy for? Merely as an object,
he is not unique?

\begin{quote}
Siriak walked about his minuscule empire and saw in passing his
omnipresent reflection at every turn.
\end{quote}

\textbf{Solitude / not being to escape himself.}

Dies, and becomes part of the island. > Bones mix with the sand ..
parrots continued to cry out his name, and it reverberated \emph{forever}

Lasting impact? Legacy? "the \emph{I} is never alone," because impact always
accompanies? Something missing in translation\ldots{}?
\end{document}
