% Created 2021-09-11 Sat 16:42
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\begin{center}
\begin{tabular}{l}
title: Eng Day One\\
course: ENG201\\
author: Huxley Marvit\\
source: \href{00-Topic-KB20200823220525.org}{00-Topic-KB20200823220525}\\
\end{tabular}
\end{center}

\noindent\rule{\textwidth}{0.5pt}

\texttt{for those reading, I had literally \textasciitilde{}30 seconds to write this.}

\section{Getting to Know You\ldots{}}
\label{sec:org945d5a7}
What do you love learning about? \emph{I love learning about philosophy,and
exploring the deeper ideas in a text.} What are you most looking forward
to this school year? \emph{I'm looking forward to the opportunity to learn
new things!} What is a favorite book or film? \emph{I don't have favorites}
What you want to work on in English class this semester? \emph{I want to work
on the flow of my essays specifically.}

\section{Essential Questions}
\label{sec:org6670f7f}
\begin{itemize}
\item How has the tools of colonialism changed
\item How do different cultures understand the relationships between
individuals and community?
\item Wifi breaking, missed the others\ldots{}.
\end{itemize}

\textbf{With Aime!} \#\#\# Think-Pair-Share - What is the diff between colonialism
and imperialism? - Goal of colonialism is to take over a place and
exploit its resources - Goal of imperialism is simply to expand the
government - What is globalization? - The connection of the globe! - The
idea of increasing interconnectivity between distinct points on the
globe - How might globalization compare with imperialism? -
Globalization is about connecting, not controlling or adding to a
current governmental system.

\section{Short Story}
\label{sec:orga8c0eda}
\href{KBTheIIsNeverAloneEnglishReadingNotes.org}{KBTheIIsNeverAloneEnglishReadingNotes} -
Short story notes
\end{document}
