% Created 2021-09-11 Sat 16:42
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Timed Closed Reading Prep}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Timed Closed Reading Prep},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Timed close reading essay prep}
\label{sec:org8f79a3a}
\subsection{General Information}
\label{sec:org0ed68d3}
\begin{center}
\begin{tabular}{lll}
Due Date & Topic & Important Documents\\
\hline
In two days & God of Small Things & God of Small Things\\
\end{tabular}
\end{center}

\textbf{Copy and paste the passage to the top of the essay!!}

\subsection{Prompt}
\label{sec:orgfb81027}
Select one of the following citations from Roy's \emph{The God of Small
Things} for your in-class close reading writing. Be sure to examine the
specific denotation and connotations of Roy's language.

\begin{verbatim}
Chacko said:
-   You don’t _go_ to Oxford. You _read_ at Oxford.
And
-   After _reading_ at Oxford, you _come down._

“Down to earth, d’you mean?” Ammu would ask. “_That_ you definitely do. 
Like your famous airplanes.”

Ammu said that the sad but entirely predictable fate of Chacko’s airplanes 
was an impartial measure of his abilities. (55)
\end{verbatim}

Reading, the double entendre. "Study (an academic subject) at a
university." (OED, AA) However, in this passage, there's also
"understand or interpret the nature or significance of." (OED, AB).

Come down --- a sense of superority --- a sense of criticism w.r.t.
Chacko has a sense of superority. Chaco's aeromodeling kit kept
crashing, shows dichotomy between reality and fiction.

Chacko's airplones, kits --- arranged --- that he always messes up.
Similar to his running of the factory. Prearranged systems that he
messes up.

Effect of sarcasm: famous. \emph{Is famous sacrasm??}

The sense of British superority used against him. Infatuation with
titles.

\begin{enumerate}
\item Infatuation with titles and male chavinism
\end{enumerate}

You don't go to oxford, you "understand" at oxford. And after you
understand at oxford, you rid yourself of your corrupt ways. One does
not simply head to oxford, one attempts to see and understand (Luke
19:5), and Come Down to rid of sins.

Inherent sense of superority, for Chacko, Oxford is the tree that allows
him to see Jesus. Marxist.

Ammu instead offers an alternate interpretation, instead of meeting a
Jesus like figure, one actually meets a harsher figure: the ground. One
acutally comes down to earth, and, instead of seeing Jesus and achiving
salvation, chacko bites the dirt\ldots{}. by destroying prebuilt systems.

Unexpected use of famous --- well known, but not because they were good
but instead because of they were expressly terriable --- offers sharp
dichotomy like that offered by Ammu before.

Highlights the contrasting nature of the sibling dynamic.

Sad --- a powerless word --- highlights Ammu's lack of control over
Chacko's falling plane. Because male superority. Because she does not
have control, she could only observe and pity.

\subsection{Claim}
\label{sec:org624dc52}
So three things

\begin{enumerate}
\item Chacko derives a sense of superiority at Oxford --- believing that it
grants him access to a hightened understading and be "saved"

\begin{itemize}
\item He does not simply read at harvard, he "reads" --- attempting to
"understand/interpreate the nature" of things at Oxford.
\item Then, after he "understands", he "comes down". This is reminiscent
as KJV Luke 19:4-5, when the greedy tax collector Zacchaeus of
Jericho climbed up a tree to see Jesus --- "to understand \ldots{} the
nature", and then got asked to "come down" b/c Jesus wants to go to
his house.
\item Chacko expected that Oxford the tree allowed him to "come down" and
be "saved" perhaps from his current station (future land lord, not
unlike Zaccheaus). However, his sister offers a different
interpretation:
\end{itemize}

\item Instead, his sister contradicts him, stating that he instead comes
"down to earth" and, instead of being saved by his Oxford education,
simply bites the dirt

\begin{itemize}
\item His family's pickle factory became unprofitable after Chacko took
over --- just like his fallen airplanes, which are boxed sets
already setup for him only for him to incorrectly assemble and
crash due to the discord that exists between his supposed newfound
hightened understanding and his actual management abilitiy.
\item Ammu remarks that the airplanes are "famous" --- really infamous.
Although not a strict verbal irony, Ammu uses the the term because
it is opposite the tipical connotation. Chacko's airplanes are
famous not for a positive quality but instead for its ease of
failure. Elongating the previous metaphore, this forshadows a
potential, infamous failure for Paradise pickles
\end{itemize}

\item Remarking upon all of this, Ammu is "sad"

\begin{itemize}
\item Sadness is quite a passive emotion --- she is unappy, and
regretful, but due to the "male chavunist nature" of society he is
unable to act
\item Ammu slightly laments her station in life this way, hinting that
she could actually see the problem clearer than Chacko as his
failure is "predictable"
\end{itemize}
\end{enumerate}

*In the passage selected in the GOST, Roy leverages biblical illusions,
creative word choices, and entended metaphores to highlight Ammu's
conflict with the 'male chauvinist' superiority exhibited by Chaco and
leverages this conflict to forshadow the eventual downfall of their
family business.*

\emph{Copy and paste the passage to the top of the essay!!}

\noindent\rule{\textwidth}{0.5pt}

There is always
\href{https://wp.ucla.edu/wp-content/uploads/2016/01/UWC\_handouts\_What-How-So-What-Thesis-revised-5-4-15-RZ.pdf}{UCLA
Writing Lab}
\end{document}
