% Created 2021-09-12 Sun 22:49
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Heart of Darkness Essay Work Doc (Jack)}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Heart of Darkness Essay Work Doc (Jack)},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Heart of Darkness Essay}
\label{sec:org58818ed}
\subsection{General Information}
\label{sec:orgaf454dc}
\begin{center}
\begin{tabular}{lll}
Due Date & Topic & Important Documents\\
\hline
Oct 13th, 1pm & Choose a recurring word, motif, pattern, or character & Well, what do you think?\\
\end{tabular}
\end{center}

\subsection{Prompt}
\label{sec:org6b96e02}
Choose a word, motif, pattern, or character that you've noticed
throughout the book, and construct an analytical, argumentative essay
around it

\subsection{Evidence bin}
\label{sec:orgb2dc5c5}
\begin{itemize}
\item /"[The African continent] had ceased to be a blank space of delightful
mystery \ldots{} it had become a place of darkness. \ldots{} But there was in it
one river especially \ldots{} resembling an immense snake uncoiled \ldots{}. It
fascinated me as a snake would a bird --- a silly little bird. \ldots{} The
snake had charmed me."/ (9) => River \emph{charm} Marlow EA
\item /"The man seemed young \ldots{} He had tied a bit of white worsted around
his neck --- Why? Where did he get it? Was it a badge --- an ornament
--- a charm --- a propitiatory act? was there any idea at all
connected with it? It looked startling around his black neck, this bit
of white thread from beyond the seas."/ (20) => Native wear \emph{charm} EB
\item /"The approach to this Kurtz grubbing for ivory in the wretched bush
was beset by as many dangers as though he had been an enchanted
princess sleeping in a fabulous castle."/ (52) => Kurts' image of
being \emph{charmed} ?? EC
\item /"The thing was to know what [Kurts himself] belonged to, how many
powers of darkness claimed him for their own. \ldots{} He had taken a high
seat amoungst the devils of the sand --- I mean literally. You can't
understand"/ (60) => Kurts as both \emph{charm} and \emph{charmer} ED
\item /"[Kurtz] began [his work] with the argument that we whites, from the
point of development we had arrived at, 'must necessarily appear to
them [savages] in the nature of supernatural beings --- we approach
them with the might as of a deity' \ldots{} From that point he soared and
took me wit him \ldots{} it made me tingle with enthusiasm. This was the
unbounded power of eloquence --- of words --- of burning nobel
words.'"/ (61) => \emph{Charming} others to \emph{charm} EF
\item /“[Kurtz] had the power to charm or frighten rudimentary souls into an
aggravated witch-dance in his honor; he could also fill the small
souls of the pilgrims with bitter misgivings./” (62) => Kurts can
\emph{charm} EG
\item /"Instantly, \ldots{} as if by enchantment, stream of human beings were
poured into the clearing by the dark-faced and pensive forest\ldots{}
[Kurtz's] thin arm extended commandingly, the lower jaw moving, the
eyes of that apprition shining darkly far in its bony head that nodded
with grotesque jerks."/ (74) => Natives are \emph{charmed} EH
\item /"He cried in a whisper at some image, at some vision --- he cried out
twice, a cry that was no more than a breath --- 'The horror! The
horror!'"/ (86) => Kurts claimed by \emph{charm} EI
\item /"''[Kurtz] had faith --- don't you see? --- he had the faith. He
could get himself to believe any thing --- anything. He would have
been a splendid leader of an extreme party'"/ (90) => Postmortum:
Kurts can self-\emph{charm} EJ
\end{itemize}

\subsection{Claim Synthesis}
\label{sec:org0d4aede}
\begin{itemize}
\item p: Establish idea of charm charm => venture into the center of charm

\begin{itemize}
\item River/land charm Marlow EA
\item Natives wear charm EB
\item Marlow thinks Kurts is charming/charmed? EC
\end{itemize}

\item p: finds kurts as both the charming and charmer => kurts propergating
this too!

\begin{itemize}
\item Kurts could self-charm EJ
\item Kurts is both charm and charmer ED
\item Kurts actively charming others to charm EF
\end{itemize}

\item p: Kurts' propergating works! => Kurts falls to his own charm

\begin{itemize}
\item Natives are charmed by kurts EH
\item Kurts claimed by charm EI
\end{itemize}
\end{itemize}

\subsubsection{Loose thoughts}
\label{sec:org7b4a8ad}
\begin{itemize}
\item Charm is an energy source
\item Its up to the enchanter --- "Kurtz" --- to channel it
\end{itemize}

\subsubsection{The Claim}
\label{sec:org3bbe685}
*Through tracking the motif of Kurtz's --- and, to a lesser extent,
Marlow's --- interaction with enchantment and its subsequent effect to
the characters in the \emph{Heart of Darkness}, the novel reveals that the
powerful and "delightful" charm of Africa could be mispurposed by
foreigners to bring crippling effects upon themselves.*

This may end up sounding racist --- Conrad warns of the potentially
crippling and reciprocal effect of the misguided exploitation of the
"charm" that exists within the African lands by Europeans. (Could
accidentally justify Conrad.)

CITE in intro/conclusion of Achebe's analysis\ldots{}

\begin{itemize}
\item Africa has inherent, not necessarily negative charm

\begin{itemize}
\item EA: it attracted Marlow there
\item EB: Marlow does not understand the spellbound natives' own ways
\item EC: getting to Kurtz was pictured as a fairytale, less as a very
sinister act
\end{itemize}

\item Kurts, the charmed and charmer, tries to channel the charm of the land

\begin{itemize}
\item EJ: Kurtz is a self-charmable prson
\item EF: The naïve Kurtz uses his charm to charm others to charm
\item ED (reverse the quote): He began acting on the charm, and Marlow
wonders what the charm will do to him
\end{itemize}

\item Kurtz's charm charms on him

\begin{itemize}
\item EH: Kurtz turned into a man of savagery by his attempted charm on
the natives (stretcher quote better?)
\item EI: "the horror, the horror" --- charm manifested as a hidden vision
--- "the horror!"
\end{itemize}
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}

There is always
\href{https://wp.ucla.edu/wp-content/uploads/2016/01/UWC\_handouts\_What-How-So-What-Thesis-revised-5-4-15-RZ.pdf}{UCLA
Writing Lab}
\end{document}
