% Created 2021-09-12 Sun 22:49
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Eng. Assess. 1 --- close reading paragraph}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Eng. Assess. 1 --- close reading paragraph},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Close Reading Paragraph}
\label{sec:org09c878e}
"Choose a short story/poem to analyze and synthesize a paragraph."

\textbf{Guiding question}: what does this aspect of the text reveal about the
broader theme of the text?

\subsection{Assessing on}
\label{sec:org5423dec}
\begin{itemize}
\item Understanding Literature: Form and Function
\item Close Reading and Argumentation
\item Structure and Mechanics
\item The Writer's Voice
\end{itemize}

Basically, anything except class citizenship.

Needs to be beyond what was discussed in class.

\subsection{Aftercare}
\label{sec:org3da0b33}
\begin{itemize}
\item 12 pt font

\item Double Space

\item 1in font

\item MLA

\item Includes Works Cited + Page Numbers based on packet page numbers.
(Citations provided on packet)

\item 8/27 --- Assessment Introduced

\item 9/3 --- Notes (close reading notes, includes 3-5 sentences that are
significant)

\item 9/8 --- Paper due
\end{itemize}
\end{document}
