% Created 2021-09-12 Sun 22:49
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{God of Small Things Essay (Jack)}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={God of Small Things Essay (Jack)},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{God of Small Things Essay}
\label{sec:orga3a1900}
\subsection{General Information}
\label{sec:org394a9c7}
\begin{center}
\begin{tabular}{lll}
Due Date & Topic & Important Documents\\
\hline
March 5th, 5PM & GoST & \emph{GoST}\\
\end{tabular}
\end{center}

\subsection{Prompt}
\label{sec:org674080a}
For this assignment, you will craft a literary analysis essay that shows
your understanding and close reading of a thematic aspect of Roy's \emph{The
God of Small Things}. As always, close reading can involve tracking a
repetition of some type in the text, including but not limited to
repetitions in diction, images, structure, syntax, or characters'
behaviors. You might also think about tracking a change of some kind in
the novel.

You may think of this analysis in two pieces:

\begin{itemize}
\item A deep engagement with textual evidence, close reading, and a thematic
scope of Roy's \emph{The God of Small Things}
\item A tracking and analysis of a pattern, theme, motif, or element of the
narrative. Your analysis MUST include the significance of this
tracking. It is not enough to notice a pattern, you must examine WHY
and HOW that pattern functions within the broader scope of the
narrative.
\end{itemize}

\subsection{Evidence bin}
\label{sec:orga48a692}
"Whole was very frequent"

\subsubsection{Holes and Smashed}
\label{sec:org35f70c4}
\begin{itemize}
\item (Holes) "Wild creepers burst through latente banks and spill across
the flooded roads. Boats ply in the bazaars. And small fish appear in
the puddles that fill the PWD potholes on the highways." AA
\item (Holes) "Steelshrill police whistles pierced holes in the Noise
Umbrella. Through the jagged umbrella holes Rahel could see pieces of
red sky." (w.r.t. communism march) AB
\item (Holes + Squash) "Vellya Paapen had assured the twins that there was
no such thing in the world as a black cat. He said that there were
only black cat-shaped holes in the Universe. \emph{/ Squashed Miss
Mitten-shaped stains in the Universe. /} Squashed frog-shaped stains
in the Universe." AC
\item (Holes) "Chacko marveled at how someone so small and undefined, so
vague in her resemblances, could so completely command the attention,
the love, the sanity, of a grown man. \emph{/ When he left, he felt that
something had been torn out of him. Something big. /} But Joe was dead
now. Killed in a car crash. Dead as a doorknob. A Joe-shaped Hole in
the Universe." AD
\item (Holes) "Estha wouldn't look up. His mind was full of trains. He
blocked the light from the door. An Estha-shaped Hole in the
Universe." (no, train was not mentioned elsewhere) AE
\item (Holes) "How marvelous!" Margaret Kochamma said. 'It's a sort of
sniffing! Do the Men and Women do it to each other too?'' She hadn't
meant it to sound quite like that, and she blushed. An embarrassed
schoolteacher-shaped Hole in the Universe.” AF
\item (Holes) "Esthappen and Rahel both knew that there were several
perpetrators (besides themselves) that day. But only one victim. \ldots{}
He left behind a Hole in the Universe through which darkness poured
like liquid tar." AG
\item (Holes) "She concealed her anguish under the brisk, practical mask of
a schoolteacher. The stern, schoolteacher-shaped Hole in the Universe
(who sometimes slapped)." AH
\end{itemize}

\subsubsection{Bottles and Cans}
\label{sec:orgbb207ef}
\begin{itemize}
\item (Bottles) "She even locked her sad, paint-flaking fridge, where she
kept her week's supply of cream buns that Kochu Maria brought her from
Bestbakery in Kottayam. And the two bottles of rice water that she
drank instead of ordinary water." (w.r.t. Baby Kochamma) BA
\item (Bottle (sealing)) "He commuted his pension and provident fund to buy
a Bharat bottle-sealing machine. Mammachi just ran it like a large
kitchen. Chacko had it registered as a partnership and informed
Mammachi that she was the Sleeping Partner. He invested in equipment
(canning machines, cauldrons, cookers) and expanded the labor force.
Almost immediately, the financial slide began" BB
\item (Cans) "His honor redeemed by his grandmother's cans, Estha Alone
organized the rusty cans of nothing in front of the urinal. He stood
on them, one foot on each, and pissed carefully, with minimal wobble.
Like a Man." BC
\item (Bottles (Closing)) "Sound of Music smell that Rahel remembered and
treasured. Smells, like music, hold memories. She breathed deep, and
bottled it up for posterity." BD
\item (Bottles, and other things.) Welp welp welp this is a quote from the
book so here goes nothing "He got a cold bottle and a straw. So he
held a bottle in one hand and a penis in the other." BE
\item (Cans) "They gave him rusted film cans in which to put the vegetables
he picked. He never bargained. They never cheated him. When the
vegetables had been weighed and paid for, they would transfer them to
his red plastic shopping basket" BG
\item (Cans) "Rahel thought of the someone who had taken the trouble to go
up there with cans of paint, white for the clouds, blue for the sky,
silver for the jets, and brushes, and thinner." BH
\item (Bottles) "The pickled mangoes had absorbed oil and expanded, making
the bottles leak." BI
\end{itemize}

\subsubsection{Eggs and Bubbles}
\label{sec:orgc5ce0d6}
\begin{itemize}
\item (Eggs) "Rahel had come to see her brother, Estha. They were two-egg
twins. “Dizygotic" doctors called them. Born from separate but
simultaneously fertilized eggs. Estha---Esthappen---was the older by
eighteen minutes.” CA
\item (Eggs) "'I tell you, these Hindus,'' Baby Kochamma said piously. 'They
have no sense of privacy' // 'They have horns and scaly skins,''
Chacko said sarcdownyastically. 'And I've heard that their babies
hatch from eggs.''" CB
\item Ok so this again. I am so sorry. (Eggs) "Then the gristly-bristly face
contorted, and Estha's hand was wet and hot and sticky. It had egg
white on it. White egg white. Quarter-boiled." CC
\item (Eggs) "The moth on Rahel's heart lifted a downy leg. Then put it
back. Its little leg was cold. A little less her mother loved her. The
Sea Queen room smelled of eggs and filter coffee." CD
\item (Eggs) "When the red cement floor [to the Ayemenem House] was laid,
the egg whites from nearly nine hundred eggs went into it. It took a
high polish." CF
\item (Eggs) "War could have been the stallion that he rode, part of, if not
all, the way to the Legislative Assembly, whereas victory left him no
better off than when he started out. He broke the eggs but burned the
omelette." CG
\item (Bubbles) "Rahel ignored her and blew an inadvertent spit bubble. Ammu
hated them blowing spit bubbles. She said it reminded her of Babà.
Their father. She said that he used to blow spit bubbles and shiver
his leg. According to Ammu, only clerks behaved like that, not
aristocrats." CH
\item (Bubbles) "Blowing through the straw (while his other hand moved),
Estha blew bubbles into the bottle. Stickysweet lemon bubbles of the
drink he couldn't drink." CI
\item (Bubbles) "So once again, in the space of two weeks, bottled Fear for
Estha. Chilled. Fizzed. Sometimes Things went worse with Coke. The
fizz went up his nose. He burped. Rahel giggled. She blew through her
straw till the drink bubbled over onto her dress. All over the floor."
CJ
\end{itemize}

\subsubsection{Misc.}
\label{sec:org5b8f19f}
\begin{itemize}
\item (Floor) "The low cement pickle vats silhouetted in the gloom made the
factory floor look like an indoor cemetery for the cylindrical dead."
DA
\end{itemize}

\subsection{Claim Synthesis}
\label{sec:org726172e}
\subsubsection{The Bin}
\label{sec:org71086a0}
\begin{itemize}
\item AA muddy water fills public works' holes in road

\item AB holes in communist umbrella reveal sky?

\item AD death as leaving a hole + leaving as tearing a hole

\item AE Estha experiences retrobution? death? by himself

\item AF British people looking down upon Indians, having been snapped at,
"dies" and gets hole-y retrobution

\item AG Valutha died as a victim, while bleeding black, rebtrobuting liquid
from his hole

\item AH Joe died, and Margret Kochamma hid that using a hole

\item BA Baby Kochamma drinks weak gruel instead of water (seeking to gain
small gains by taking the wastewater of rice cooking)

\item BB Industrial botteling machine for sealing bottles leads to financial
slide

\item BD smell of movies bottled up for memories

\item BE abuse as balance between bottle and um\ldots{} that other thing

\item BF Rahel "canned" by principle due to her childlike nature

\item BG silent Estha places vegetables in film cans

\item CB Chacko sarcastically relates babies of Hindus as being from eggs

\item CC abuser having given Estha eggs

\item CD sad sea queen where Rachel is loved less smelt of eggs

\item CF egg whites as polishing the ground floor of house

\item CH spit bubbles reminds Ammu of the twins' degenerate father

\item CI Estha blew bubbles into abuser's drink

\item CJ bubbled cold drink as fear

\item DA Factory floor as gloomy after family is seperated
\end{itemize}

\subsubsection{The Synthesis}
\label{sec:orga247d6d}
\subsubsection{Bottles Contain Emotions}
\label{sec:org145236c}
Fear was handed to Estha bottled in Two Bottles:

BE abuse as balance between bottle and um\ldots{} that other thing. Which is
also a bottle. Think about it a little bit harder.

\begin{itemize}
\item CJ first, bubbled cold drink as fear. (maybe the other (sickly sweet)
quote?)
\item Of half-cooked eggwhites --- of deformed love. => CC abuser having
given Estha eggs as a product of love.
\end{itemize}

\subsubsection{Bottled Emotions are Handled to Little Gain}
\label{sec:org9703a6b}
Items, once bottled up, are frequently handled by characters
overprotective of the bottled emotions in order to gain often minimal
results.

BA Baby Kochamma --- the opportunist that also looses the big picture
--- drinks weak gruel locked away instead of water (seeking to gain
small gains by taking the wastewater of rice cooking) --- literally
valuing the wastewater of a paulper.

In order to proof his manhood, Estha BC attempting to carefully ride
above emotions (cans). This restraint of emotions ("sing outside"), of
course, lead to him being abused.

\subsubsection{The Bottling Process Ultimately Leads to Downfall}
\label{sec:orgca259da}
Right before the abuse, Rahel attempted to capture the final reminants
of her positive emotion into a "bottle", BD smell of movies bottled up
for memories. Unfortunately, this did not end well with the abuse.

BB Industrial botteling machine for sealing bottles leads to financial
slide: mass-processing emotions does not land well => DA Factory floor
as gloomy after family is seperated --- lack of love, of egg-whites that
shone the floor CF

*Through tracking characters' use of the bottle as an instrument to
preserve strong emotions in the \emph{God of Small Things} --- namely, that
of love, as represented by the Egg, and of fear, as with Bubbles --- the
novel paints a cautinary tale against the forcible containment of raw
emotions which will lead to a depressive and gloomy downfall.*

\noindent\rule{\textwidth}{0.5pt}

There is always
\href{https://wp.ucla.edu/wp-content/uploads/2016/01/UWC\_handouts\_What-How-So-What-Thesis-revised-5-4-15-RZ.pdf}{UCLA
Writing Lab}
\end{document}
