% Created 2021-09-12 Sun 22:49
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{ISOS Story Research}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={ISOS Story Research},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Alan Turing (1912-1954)}
\label{sec:orgf121e32}
Alan turing was a mathematition and chyptographer who worked to break
German encryption and ciphers during WWI and established a series of
theories on algorithmic computability.

\subsection{Work at Combridge Regarding Computability (1936-1938)}
\label{sec:org3b314a2}
Turing crated proof that a "universal computing machine", as defined by
specific parametres, could compute any mathematical operation as long as
it is algorithmically representable.

Furthermore, he showed that there are no solutions to the base-case
decision problem (finding the provability of an theorem based on only
axioms in O(1) time) because his "computing machines" could not have a
finite state by when they halt.

\subsection{Hut8 (1938-1941)}
\label{sec:orgd05fa89}
Turing invented a system to decode German communication ("Enigma") with
a rotating weights sytem in the Hut8 program at Bletchley Park; however,
Turing did not support the method by which the US navy decided to
execute upon codebreaking. His codebreaking efforts, by estimate, shaved
2 years from the war.

He also assisted in creating secured speech systems for the navy.

\subsection{Turing test (1945-1947)}
\label{sec:org00bfefa}
Alan turing became interested the problem with artificial intellingence,
and proposed the "turing test" as a way of seggregating AI with humans.

\subsection{Capture, prosecution, and Death (1952-death 1954)}
\label{sec:org6042c46}
\noindent\rule{\textwidth}{0.5pt}

\section{Context and Science of Turing's Discoveries}
\label{sec:orgc91ce96}
Turing's career really spanned three different phases: his work on
computability, his coding work at Hut8, and finally his brief stint of
interest in artificial intelligence. There are different contexts under
which each of these discoveries took place, with the war work being the
centrepiece of his claim to international fame.

\subsection{Computability}
\label{sec:org3786306}
In the early days of Turing's academic life, he worked in the early
beginnings of computer science --- then still a form of "mathematics."

As the study of "algorithums" (which evolved to be the foundation of CS)
was gaining popularity among mathematitians; Turing published his work
on "Computable Numbers" and created hypothetical devices named "turing
machines" that would solve any agrothmic problems.

These "turing machines", and the theory thereof, eventually became the
foundations for the definition of a programming language --- that any
language sufficient to emulate a turing machine will then be capable to
solve any algorthimic problem or implement any program.

This, in addition to the lack of solution for the "halting problem" with
Turing machines which implies the inability to solve the decision
problem, showed the necessity of proofs (that proofs could not be
"inferred" and has to be "computed".)

\subsection{Hut8}
\label{sec:orgccff77a}
Under the context of WWII, Turing worked at Government Code and Cypher
School, working on the cryptoanalysis of the Enigma machine.

Turing is perhaps best known for his work in the cracking the German
Naval Enigma --- solving first the naval indicator system by which the
enigma machines communicate in 1939 and returning to Blenchley Park
in 1943.

Hugh Alexander, the head at Hut8, supposed that Hut8's sucess is largely
attributed to the work of Turing.

Because of his work to break effective German code, Turing likely
resulted in the shortening of the war and prevented thousands of deaths.

\subsection{Turing Test}
\label{sec:org2c9fa9b}
After his work at Hut8, Turing retained a government advisory job and
started returning to academia in development of early stored-program
computers (the ACE: Automatic Computing Engine). However, he was later
found guilty of homosectuality and commited\ldots{} Suiside? or Accidental
Poising? shortly thereafter.

With the dawn of computer programs, Turing began exploring the idea of
computed intelligence: creating a philosophical "Turing Test" by which
one could mark the standard for computed intelligence.

Turing also proposed the idea of self-improving computation, that: its
"easier to build a child mind and subject to education than bulding an
adult mind".

The turing test became a fundimental concept in the bourgening field of
Artificial intelligence, and the reversed form of the Turing test ---
the CAPCHA --- is widely deployed today.
\end{document}
