% Created 2021-09-12 Sun 22:49
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{ISOS ML Privacy}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={ISOS ML Privacy},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#ref \#ret

\noindent\rule{\textwidth}{0.5pt}

\%\%- n: usa foreing intel survelance - j: edward snowden, apple data
collection. consumer notification! - d: digital polical ads + tracking -
m: social media taking data in general - h: human ml modeling \%\%

\section{Page o' notes}
\label{sec:org67e5ec4}
\subsubsection{Machine learning broad level implications on privacy}
\label{sec:org6b4ad02}
\begin{itemize}
\item ML requires big data

\begin{itemize}
\item machine learning has driven us into the "information age"

\begin{itemize}
\item cause of most of these issues
\end{itemize}

\item getting lots of info -> invading privacy, generally
\end{itemize}

\item ML can break privacy without explicit data

\begin{itemize}
\item ML can de-anonymize anonymous activities

\begin{itemize}
\item ML based tracking systems make anonymity hard
\item hashing ISN'T good enough
\end{itemize}

\item same thing can be done even without ml

\begin{itemize}
\item location tracking easily de-anonymized by simple cross reference
\end{itemize}
\end{itemize}

\item ML can construct human models

\begin{itemize}
\item fundamentally about simulation intelligent behavior
\item ML model of how you think and act

\begin{itemize}
\item viewed as creepy
\end{itemize}

\item if it could predict your thoughts, what then?
\end{itemize}
\end{itemize}

\subsubsection{Regulation!}
\label{sec:orgdc72af5}
\begin{itemize}
\item FTC (federal trade commission) coming down hard

\begin{itemize}
\item hitting Facebook, google, ect.
\end{itemize}

\item CCPA, California consumer privacy act
\item GDPR, General Data Protection Regulation
\item how effective is regulation?

\begin{itemize}
\item can we really prevent it?
\item one of the arguments: > "if you make data collection illegal, only
criminals will have the data"
\end{itemize}
\end{itemize}

\subsubsection{Rights}
\label{sec:org01e4c92}
\begin{itemize}
\item right to be forgotten

\begin{itemize}
\item opt out law by the consumer
\item is this a right?
\end{itemize}

\item right to our data, as outlined in CCPA

\begin{itemize}
\item again, really a right?
\end{itemize}

\item individualize experience moral?

\begin{itemize}
\item amazon adjusting prices,
\item insurance companies not accepting
\item ect.
\end{itemize}

\item private company rights to charge how they please?

\begin{itemize}
\item \textbf{libertarian args go here}
\end{itemize}
\end{itemize}

\subsubsection{Flipside}
\label{sec:org35a62e5}
\begin{itemize}
\item if privacy-preserving techniques ultimately fail,

\begin{itemize}
\item then what?
\end{itemize}

\item ML does a lot of good

\begin{itemize}
\item though the individual might not want to share medical data,
\item that same data on the large scale could save countless lives
\end{itemize}

\item garbage in, garbage out + black box

\begin{itemize}
\item not. good.
\item especially when AI will dominate decision making and analysis.
\end{itemize}

\item forced to give data by tragedy of the commons

\begin{itemize}
\item you want ml networks to portray your demographic accurately,
\item and if you don't give data, it won't. In a world dominated by ml,
\item giving your data becomes necessity
\end{itemize}

\item forced to give data by economic necessity

\begin{itemize}
\item where data collection is truly opt out, services replace it with
paid
\item economically worse off will be more likely to give data
\item skews data collected?
\end{itemize}
\end{itemize}

\subsection{during discussion}
\label{sec:org94b390e}
pri v sec -> pri v los

\subsection{Reflec}
\label{sec:org0418712}
\begin{enumerate}
\item *What is the ethical issue/debate/controversy in question? In other
words, how does the topic relate to the question of how we should
live with science and technology?* Should abortion be legal? How do
we think about start of life with improving technology?

\item \textbf{Describe at least two different perspectives on the issue (these
could be complementary or opposing).} Abortion is murder, it shoudn't
be legal. People have a right to their own body.

\item \textbf{What seems to be at stake (e.g, philosophically, politically, or
intellectually)?} Abortion laws!
\end{enumerate}
\end{document}
