% Created 2021-09-27 Mon 12:01
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley Marvit}
\date{\today}
\title{Notes on Hannah-Jones 1619 Project}
\hypersetup{
 pdfauthor={Huxley Marvit},
 pdftitle={Notes on Hannah-Jones 1619 Project},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\#flo \#inclass

\noindent\rule{\textwidth}{0.5pt}

\section{critical :clap: race :clap: theory}
\label{sec:org280c823}
\href{https://docs.google.com/presentation/d/1mt\_EI52yOI\_1CjRTvtsrB03vBC-SVn5SE1etnyqeAg4/edit\#slide=id.p}{slides}
\href{https://docs.google.com/document/d/1wK9TJp4Nhl5z4uEl7i-OoU0ccDv-MuWXdB75lPd1-Wg/edit}{reading}
notes: \href{KBxHannahJones1619Project.org}{KBxHannahJones1619Project}
\href{KBx1619ProjectTookOver2020.org}{KBx1619ProjectTookOver2020}

\begin{verbatim}
1. What would you descirbe as Hannah-Jones's goal in her introduction?
2. Is Hannah-Jones creating the progessive narrative that Cowie is calling for or is the 1619 prioject an example of anti-patriotism on the left?
\end{verbatim}

\begin{enumerate}
\item make herself infallable?
\item anti-patriotism. no options to solve

\begin{enumerate}
\item nvm, she acknolgeses that things get better, therfore america is
not doomed.
\end{enumerate}
\end{enumerate}

cowies anti-patriotism: america is bad, and we can't solve it.
fundemental: views it as solvable or unsolvable redeemable vs. solvable
past vs future

\begin{verbatim}
Cosmopolitanism can be defined as a global politics that, firstly, projects a sociality of common political engagement among all human beings across the globe, and, secondly, suggests that this sociality should be either ethically or organizationally privileged over other forms of sociality.
\end{verbatim}

\begin{itemize}
\item to be authentic responsible scholars: start with the text, then go
into criticisms.

\begin{itemize}
\item can't critique until you understand her ideas
\end{itemize}

\item thesis: black americans fought for freedom and paved the way for
others freedom
\end{itemize}

mythology vs story -- used by tom

\begin{itemize}
\item civil rights act:

\begin{itemize}
\item patriotism by descent
\end{itemize}

\item special place for descent in our culture

\begin{itemize}
\item celebrating tradition of descent
\end{itemize}

\item the facts are not the intresting controvery

\item CRT emerged in the 80-90s

\begin{itemize}
\item started in legal studies, moved into public policy
\end{itemize}

\item deals with: why do we have sytemic racism if we dont mention race in
our legal system?

\item argues, we need more than race neutral conversation / terminology

\begin{itemize}
\item racists shaped more than the slavery itself?
\end{itemize}
\end{itemize}
\end{document}
