% Created 2021-09-27 Mon 12:01
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Japanese Self Eval}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Japanese Self Eval},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\#ret

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
Please reflect on your learning this past semester in the following areas.  Write a few sentences for each question (#1-3).  You don’t have to answer all the sub-questions; they are just suggestions.  Please answer in English.
\end{verbatim}

\begin{enumerate}
\item Highlights
\end{enumerate}

One highlight was the oral exam --- not the exam itself, but the process
of studying for the exam. While incredibly stressful and a massive
amount of work, it felt good to finally be able to put everything we
have learned this semester to use.

\begin{enumerate}
\item Challenges
\end{enumerate}

Some of the early listening quizzes were quite challenging for me, as
the audio was not nearly as clear as in person. I was also just getting
used to the whole quarantine schooling situation, which is much
different than last year.

\begin{enumerate}
\item Goals
\end{enumerate}

My goals were to try to become more 'fluent,' in the sense that the
barrier between meaning and sentence in Japanese is reduced. I
definitely do feel that I have reduced this barrier quite a bit. In the
next semester, I seek to continue to reduce this barrier.

\begin{enumerate}
\item Do you have any other questions, comments, or requests for me?
\end{enumerate}

Despite the constant barrage of apocalypses (apocali?), it has been a
wonderful semester of Japanese!
\end{document}
