% Created 2021-09-27 Mon 12:00
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Houjun Liu}
\date{\today}
\title{Triggering WWI}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={Triggering WWI},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents



\section{Wartime Tensions: Triggering WWI}
\label{sec:orge9046f3}
\subsection{Slavic Natinoalism}
\label{sec:org4172ebf}
Slavic nationalists believe that Germanic Dual-Monarchy will not grant
them enough rights as a culture, so nationalism caused part of Austria
to want to join Serbia.

CLAIM @\href{KBhHIST201PalmerCh17.org}{KBhHIST201PalmerCh17}: the
alliance system is a sign of deeper issues caused by the fact that the
world had a globalized economy buit with a national-level governance;
each government is economically dependent but ideologically independent
so must compete to get resources and form alliances to bolster security

\begin{html}
<!-- Overall, Germany’s latecoming to world power drove the basic cause of war. -->
\end{html}

\noindent\rule{\textwidth}{0.5pt}

Before we continue, a crash course on Realism.

\href{KBhHIST201Realism.org}{KBhHIST201Realism}

\noindent\rule{\textwidth}{0.5pt}

19th century status quo was challenged when the HRE failed to recognize
the collective.

\subsection{Diplomatic collapse}
\label{sec:orgb21ee9f}
Two things lead to the final displomatic collapse\ldots{}

\begin{enumerate}
\item Young Turks forced the Ottoman sultan to restore parlimentary
constitution, and invited delegates from Bosnia + Bulgaria to
participate
\item Russia, failing to control Japan, seeked control of Constantenopal.
\end{enumerate}

Russian and Austrian foreign ministers agreed to call a confrence to
annex Bosina. But, Austria did it before actually colling the confrence,
which lead to the unhappiness of the serbs (who wanted Bosinia) even
more grumbly. Rrussian public opinion stands with Bosnia + the Serbs
even if its government is secretly plotting against them.

Italy declared war on Turkey, embarissing the ottomans. This caused a
series of effects w.r.t. the Serbs that lead to two Balkan wars.

Serbs, Greeks, and Austrians each tried to advocate their own
interested, eventually resulting an agreement of peace and an
indipendent Albanian kingdom --- which\ldots{} made everyone unhappy.

Claim: \textbf{a third Balking crisis caused the war: Austra feels exasperated,
Serbs feel Deperate, and Russians feel humiliated.}
\end{document}
