% Created 2021-09-27 Mon 12:01
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{svg}
\usepackage{cancel}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\renewcommand{\tableofcontents}{}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{McNeill Reading Notes}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={McNeill Reading Notes},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\#flo

\section{Europe's Self-Transformation}
\label{sec:org2038671}
Main thrust of development: politics.

Power was concentrated

Each region or so had its own ruler, and was bordered (ish), but they
were connected by a single center.

\begin{quote}
political consolidation
\end{quote}

Bunch of wars fought around religion.

Consolidation "reflected" massive advances in military technology.

What do they mean by reflected? Like advanced, but they cant say for
sure? like happened at the same time, but causation is unclear?

Weapons become better and more powerful, organization and resource
allocation becomes more important

This forced more centralization?

Bunch of names and dates lacking concepts

Religious worries started to re-emerge after the renaissance

Many of the changes that happened to Europe were started (catalyzed?) by
religious controversy.

Bunch of tech increase despite religious wars

Science did not oppose religious beliefs, necessarily

\section{Perceived importance of universal agreement decreased}
\label{sec:orge012650}
\texttt{=intellectual pluralism baby!=}

In class jots:

during a time of significant change and growth -- was the first sort of
highly interconnected region?
\end{document}
