% Created 2021-11-05 Fri 09:33
% Intended LaTeX compiler: xelatex
\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\author{Houjun Liu}
\date{\today}
\title{National Period}
\hypersetup{
 pdfauthor={Houjun Liu},
 pdftitle={National Period},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.50 (Org mode 9.4.6)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

The Early Part of the United States' History! "Does not get you through your SAT."

\section{The Earliest Presidents}
\label{sec:org87e0ae3}
\begin{itemize}
\item Washington
\item Adams
\item Jefferson
\item Madison
\item Monroe
\end{itemize}

\section{Westward Expansion}
\label{sec:org6cc5558}
Always assumed that they would expand west and take rights from the Indians. The \textbf{\textbf{second amendment}} was as much about bearing arms against Indians than it is about bearing arms against the British.

\subsection{Getting Texas}
\label{sec:org4825985}
James Polk leveraged the Mexican-American war to acquire the new Western technology.

\subsection{Louisiana Purchase}
\label{sec:orga15a395}
Did not actually have authority to do so, but just did it kind of for funzies.

\section{Federalism vs Anti-Federalism}
\label{sec:orgbd0040e}
The perspectives of the new ideas remain. \emph{John Adams} was a pretty large power grabber to solidify the federalist position. Pushing Virginia and New York to ratify was a pretty large point because they have the biggest negotiating point.

\section{The Executive}
\label{sec:org80620ac}
Washington gave a lot of precedents to the presidents.

\begin{itemize}
\item Served two terms \& steps down: does not try to take over
\item Set a tone and expectation that presidents will not live their whole life in power
\item \textbf{\textbf{Advised to avoid the fight between France and England}}
\end{itemize}

\subsection{Washinton}
\label{sec:org5fe6a31}

\subsubsection{Wiskey Rebellion}
\label{sec:orga4f44cf}
A rebellion rose against taxes of the Whiskey. Washinton's leadership and success in putting down the rebellion offers sharp contrast to the Articles' handling of Shay's Rebellion.

\subsubsection{Dealing with Native Americans}
\label{sec:org0ec6448}
Washinton dealt with the NAs by chasing them out into newly-treaties land via leveraging the military.

\subsubsection{Hamilton's Financial Programs}
\label{sec:orgba01361}

\begin{enumerate}
\item Fixing Problems
\label{sec:orgdb1f0b0}
\begin{itemize}
\item Pay of all war debts
\item Raise revenue
\item Create a central bank
\item Most southern-states opposed northern states debts being paid off
\item \textbf{\textbf{capital in the south}}
\end{itemize}

\item L'Enfant Plan
\label{sec:org7b21d0a}
Washinton D.C., with its grid layout and diagonal streets, was quite a master-planned city.
\end{enumerate}

\subsection{Adams}
\label{sec:org21458da}
Did not endear himself to others, and was quite a short stature. Was not quite benefited by the fact that Washington --- who was tall and polished.

\subsubsection{Alien and Sedition Acts}
\label{sec:org52e17bd}
Got a lot of criticism by acts to exclude aliens from voting and preventing people from criticizing the government.

\subsubsection{XYZ Affair}
\label{sec:orga94f5c3}
France wanted America to force a bribe before they would see the American ambassador.

\subsubsection{Virginia \& Kentucky Resolutions}
\label{sec:org2c76c21}
Two different parties was leading and vice-leading. Jefferson was trying to jab the president in the back: trying to nullify federal law.

\subsection{Jefferson}
\label{sec:org4c805e2}
"Democratic Republican party": identify difference with the elite Federalists. Plantation owner with two families (look it up!).

\begin{itemize}
\item Among the political and economic elite in the US
\item Wins the election, and inherits justices that were Federalists
\end{itemize}

Tells Madison to ignore Jefferson. The \emph{Marbury v. Madison} is declared unconstitutional: which then solidifies the standing of the court as a group to interpret the laws. Jefferson was furious, as this expanded the power of the Judicial branch. But he did not wish to take action because if he did than Marbury would win.

\subsubsection{Louis and Clarke}
\label{sec:orgd525b4a}
Looking for the water root of the Missouri River.

Flipped over the Rockies to hope to find the ocean, but no. It is not the ocean: its more land! They carried on, traded with the Native Americans for sustenance, and finally reach the Pacific Coast.

York, their slave, gets here the first vote to make the decision whether or not to return after the Pacific. The wife of a Frenchmen helped navigate the diplomacy of the group and translates. She helped create the opportunities for trade.

They make it back alive.

\subsubsection{Louisiana Purchase}
\label{sec:org2e61ee6}
Naepolean needed money.

\subsection{Madison}
\label{sec:org0d3f6a7}
War of 1812 hits, US was at war with England to get Quebec. Naepolean was defeated in Europe, and DC was eventually burned. Also Andrew Jackson was fighting this war.

\subsection{Monroe}
\label{sec:org8567911}
The Missouri Compromise tries to keep the senate balance by bringing Maine as a free state: creating a 36*30 line. Monroe Doctrine: tried to push out England and France and will protect Latin America; this would therefore establish hegemony and a sphere influence ("England protected the 13 colonies, too.")

\section{Characterizing the Antebellum Period}
\label{sec:org006e27d}
\subsection{A note on characterization things}
\label{sec:orgc339843}
Remember: characterization is something tangential.


\subsection{Social Changes}
\label{sec:orgf8aee37}
\begin{itemize}
\item Women's Roles: limited freedoms \& limited access to upper-class education
\item Free African Americans in the North --- had freedoms and had no political/civil rights
\item Second Great Awakening: religious ideas in the Americas transforms
\begin{itemize}
\item Huge revival period of religions (like the '60s, '70s, '80s)
\item Pushing for things to reform society
\end{itemize}
\end{itemize}

\section{The Divided Antebellum}
\label{sec:org9fec7f4}
The National period could be said to be a process that's quite divided, building up to the war.

\textbf{\textbf{Nationalism and Revolution are the two sides of a coin}}

\begin{itemize}
\item Remembering: the \emph{rebellion} after the British in the \emph{nationalism} in the US
\item So, is the internal-to-American rebellions also an act of Nationalism?
\end{itemize}

\subsection{Themes of the Antebellum}
\label{sec:org5cac159}
\begin{itemize}
\item Age of Genocide (Madley): native american killings
\item Age of Abolition (Garland): civil war buildup
\item Age of Andrew Jackson (Schlesinger): he's epic
\item Age of Technological Revolution (Howe): tech happens always, its just tech influencing politics
\item Era of Reform (Walters): reforms happens all the time, though
\item Age of Immigration (Seller): globalization and huge global migration
\item Evolution of Democracy (Boek): we are getting better as a democracy, right?
\end{itemize}

\subsection{The Age of Division}
\label{sec:orgc021153}
\begin{itemize}
\item \textbf{\textbf{Dis-union}} is also noting new!
\begin{itemize}
\item 13 isolated English colonies
\item Failed Albany Plan of Union, 1754
\item Confederation of Sovereign States
\item Sectionalism: Northeast, South, west --- leads states to want to leave the union
\item Anti-Federalists vs. Ratification
\end{itemize}
\end{itemize}

Rhode Island did not want to join, NY did not ratify until very late.

\subsubsection{The Secessionitis}
\label{sec:org58bb390}
\begin{itemize}
\item 1814 at the \textbf{\textbf{Hartford Convention}} -- long before the civil war -- several Northeastern states plan secession until Jacks'n victory
\item South Carolina \textbf{\textbf{nullified}} federal laws
\end{itemize}


\subsection{Rebellions going on}
\label{sec:orgc5b2085}
That it is the \textbf{\textbf{rebellions}} that caused the increased nationalism

\begin{itemize}
\item Bacon's Rebellion
\item Shay's Rebellion
\item Ratification crisis
\item Whiskey Rebellion
\end{itemize}

Latin-American revolutions soon followed the American Rebellion. 

\subsection{National Unities}
\label{sec:org7057aea}
\begin{itemize}
\item Apparent Victory in War of 1812
\item Monroe Doctrine of 1823 - not only are we unified, we would control the hemisphere
\end{itemize}
\end{document}