% Created 2021-09-11 Sat 08:16
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Exr0n}
\date{\today}
\title{Calculus Introduction with Nas}
\hypersetup{
 pdfauthor={Exr0n},
 pdftitle={Calculus Introduction with Nas},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle


\section{Math Is}
\label{sec:orgd2d3520}
\begin{itemize}
\item "\ldots{}take a moment to delight in the question itself;"
\item Inspirations

\begin{itemize}
\item Measurement | paul lockhart
\item the jazz of physics | Stephon Alexander
\end{itemize}
\end{itemize}

\subsection{Advice}
\label{sec:org4136f27}
\begin{itemize}
\item the best problems are your own
\item collaborate
\item let it be hard. try not to get discouraged or to take your failures
too personally.

\begin{itemize}
\item just be yourself and go where you want to go. instead of being
tentative and fearing failure or confusion, try to embrace the awe
and mystery of it all and joyfully make a mess
\end{itemize}

\item do not ignore symmetry "a proof is simply a story\ldots{} the plot not only
has to make logical sense but also be simple and elegant."
\item improve your proofs; critique your work, let a problem take you where
it takes you
\item try things. Guess. As you do more math, your intuition and your
instincts will sharpen\ldots{}to provide \emph{sensitivity to structure}
\end{itemize}

\subsection{Interdisciplinary Cross Fertilization}
\label{sec:orgd7d1e6b}
\begin{itemize}
\item borrow analogy from what "might, at first glance, be a complexly
unrelated discipline."
\item "it is in the \emph{limits} of these analogies where there exists a need
for further research."
\item "what are you getting at?" "I don't know."
\end{itemize}

\subsection{Book Recommendations}
\label{sec:org4d353e7}
\begin{itemize}
\item Journey through Genius
\end{itemize}

\subsection{Syllabus}
\label{sec:orgafd3db3}
\href{KB202008250952.org}{KB202008250952}

\subsection{Collaboration}
\label{sec:orgb67c28a}
nnazerali@nuevaschool.org

You should advocate for yourself and schedule 1 on 1 meetings even when
you aren't struggling. This should happen every other week or so.

Nas is free from blocks 1-4 + tutorial times.

\subsection{For Next Class}
\label{sec:orgdc9c8ab}
\begin{itemize}
\item Reccomended reading [[\url{.org}][]]
\item Math/Calculus books, videos
\end{itemize}

\noindent\rule{\textwidth}{0.5pt}
\end{document}
