% Created 2021-09-11 Sat 08:16
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Dont read this man}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Dont read this man},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#ret

\noindent\rule{\textwidth}{0.5pt}

\begin{verbatim}
Write one or more paragraphs about your academic habits of learning so far this
semester. What have you been doing well? What can you improve?
Aspects you could consider include: participation in class and contributions to the learning environment, productivity and engagement in class (whether in whole-class discussion, or collaborating in breakout rooms), organization of work, maintaining notes, timely submission of homework assignments, incorporating feedback on your work, making corrections to
your notes and homework, asking questions and practicing self-advocacy, etc. You should
also describe your level of effort on assignments and homework and your willingness to try challenges.
\end{verbatim}

The semester thus far has been an incredibly strange experience. It is
my first entirely remote semester, with almost no one that I knew before
the lock-down. While I'm active in breakout rooms, this makes it harder
to participate in class discussions. I would like to work on this. In
breakout rooms, we all work together in and out of class to better each
others understanding. Just like in-person classes, I have worked hard to
understand the material well and turn in my work on time. At times on
the homework I have felt 'burnt out' in a sense after doing multiple
pages of essentially the same question, leading to me not feeling up for
completing the bonus problems. This is something I would like to problem
solve. I have not yet received a lot of feedback on my work, but when I
do, I will be happy to incorporate it. As for my willingness to try
challenges, I am actually more willing (or more excited) to try
challenges rather than 'normal' problems. I find them a lot more
interesting. All in all, so far I think this has been a great semester,
and I'm looking forward to the rest of it!
\end{document}
