% Created 2021-09-11 Sat 16:41
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley}
\date{\today}
\title{Ethical Concerns}
\hypersetup{
 pdfauthor={Huxley},
 pdftitle={Ethical Concerns},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\#flo \#disorganized \#incomplete

\noindent\rule{\textwidth}{0.5pt}

\section{Can we get back to coding}
\label{sec:orgf9ead05}
please? yaow.

\noindent\rule{\textwidth}{0.5pt}

\begin{itemize}
\item Privacy

\begin{itemize}
\item Good ml requires lots of data, so inherent leads to violation
\item Also, algorythym predicts private things?

\begin{itemize}
\item Target example.
\end{itemize}
\end{itemize}

\item Bias

\begin{itemize}
\item \begin{quote}
Our model has bias built into them
\end{quote}

\begin{itemize}
\item ex. prop 25

\begin{itemize}
\item get rid of bail, and use ml to identify flight risks
\item has bias in the model due to a biased dataset
\end{itemize}
\end{itemize}

\item Input bias -> output bias
\end{itemize}

\item Abuse and misuse

\begin{itemize}
\item Using ml in ways that are morally wrong

\begin{itemize}
\item Ex. Cambridge analytica

\begin{itemize}
\item Put up quizes, then sold data to companys which put targeted
adds to swing votes.
\end{itemize}
\end{itemize}
\end{itemize}

\item Model explanability

\begin{itemize}
\item Don't know how to explain results
\end{itemize}

\item Responsibility

\begin{itemize}
\item Sold model to someone who used it for abusive use / it just breaks

\begin{itemize}
\item Who is at fault?

\begin{itemize}
\item Model builder? Data collector? Abuser?
\end{itemize}

\item Large problem for things that are "literally life or death"

\begin{itemize}
\item Watson, what happens when it's wrong?
\end{itemize}
\end{itemize}
\end{itemize}

\item Automation of labor

\begin{itemize}
\item Putting people out of jobs
\item More existential: what will people do? When ml does everything
better than us
\item sudo-creative work is already being done
\end{itemize}

\item Existential risk

\begin{itemize}
\item Essentially, terminator risk
\item Or, morality is not encoded into ml for task optimization

\begin{itemize}
\item ex. make a class happy,

\begin{itemize}
\item human: fun activity
\item ml: inject morphine
\end{itemize}

\item Paperclip

\begin{itemize}
\item primary directive of producing paperclips
\item ignores morality
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\end{document}
