% Created 2021-09-11 Sat 08:17
% Intended LaTeX compiler: xelatex
\documentclass[letterpaper]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{indentfirst}
\setmainfont[ItalicFont = LiberationSans-Italic, BoldFont = LiberationSans-Bold, BoldItalicFont = LiberationSans-BoldItalic]{LiberationSans}
\newfontfamily\NHLight[ItalicFont = LiberationSansNarrow-Italic, BoldFont       = LiberationSansNarrow-Bold, BoldItalicFont = LiberationSansNarrow-BoldItalic]{LiberationSansNarrow}
\newcommand\textrmlf[1]{{\NHLight#1}}
\newcommand\textitlf[1]{{\NHLight\itshape#1}}
\let\textbflf\textrm
\newcommand\textulf[1]{{\NHLight\bfseries#1}}
\newcommand\textuitlf[1]{{\NHLight\bfseries\itshape#1}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{titlesec}
\usepackage{titling}
\makeatletter
\lhead{\textbf{\@title}}
\makeatother
\rhead{\textrmlf{Compiled} \today}
\lfoot{\theauthor\ \textbullet \ \textbf{2021-2022}}
\cfoot{}
\rfoot{\textrmlf{Page} \thepage}
\titleformat{\section} {\Large} {\textrmlf{\thesection} {|}} {0.3em} {\textbf}
\titleformat{\subsection} {\large} {\textrmlf{\thesubsection} {|}} {0.2em} {\textbf}
\titleformat{\subsubsection} {\large} {\textrmlf{\thesubsubsection} {|}} {0.1em} {\textbf}
\setlength{\parskip}{0.45em}
\renewcommand\maketitle{}
\author{Huxley Marvit}
\date{\today}
\title{Phys Day One}
\hypersetup{
 pdfauthor={Huxley Marvit},
 pdftitle={Phys Day One},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\noindent\rule{\textwidth}{0.5pt}

\begin{enumerate}
\item Intro:
\label{sec:org8bf2ae1}
\begin{enumerate}
\item Something that

\begin{enumerate}
\item was surprising,
\item was disappointing,
\item and was exciting
\end{enumerate}
\end{enumerate}

\emph{ft. bron? \#why.}

oml we did \textbf{three intros each.}

\noindent\rule{\textwidth}{0.5pt}
\end{enumerate}

\section{What we are learning:}
\label{sec:org9ebf665}
\begin{quote}
"best way to learn is to teach"
\end{quote}

ie. ask peers for help, not barak.

\begin{itemize}
\item Physics tried to describe things completely with math, unlike other
sciences which use statistical models.
\item Semester one:

\begin{itemize}
\item kinematics!
\item Projectile motion
\item Dynamics!
\item Energy (defines all of physics, but we don't really know what it is)
\item Momentum
\item Maybe: rotational motion
\end{itemize}

\item Around 30 min per class
\end{itemize}

\subsubsection{Grading:}
\label{sec:org16d1b20}
\begin{itemize}
\item Aim for profs. Profs are an a. But ofc, go for exemplery!
\item Lots of quizzes
\end{itemize}

\section{The map of physics}
\label{sec:orgfab9ad1}
\begin{itemize}
\item Classical

\begin{itemize}
\item Newtons Laws of motion and universal gravitation

\begin{itemize}
\item Also worked on optics,

\begin{itemize}
\item Waves and cosmology and astrophysics
\end{itemize}
\end{itemize}

\item Electromagnetism
\item Classical and fluid dynamics
\item Fluid dynamics
\item Chaos Theory
\item I'm not going to take notes in this
\item \^{} in the 1900s
\end{itemize}

\item Relativity

\begin{itemize}
\item Special relativity

\begin{itemize}
\item Light is at a constant speed to all viewers
\end{itemize}

\item General relativity
\end{itemize}

\item Quantum Physics

\begin{itemize}
\item Nuclear physics
\item Particle physics
\item quantum field theory | ties in with special relativity
\end{itemize}

\item The Chasm of ignorance

\begin{itemize}
\item we can't connect general relativity to quantum physics
\item Also, dark matter and dark energy and such
\end{itemize}
\end{itemize}

Black = 101 Red = 201
\end{document}
